### 2016-04-10 presentation/presentation.tex
finish summarizing LDA results

% \documentclass[14pt]{beamer}
\documentclass[handout,14pt]{beamer}

\usepackage{pgfpages}  % Uncomment one of these lines for X-on-1 printing
% \pgfpagesuselayout{4 on 1}[letterpaper, border shrink=5mm, landscape]
% \pgfpagesuselayout{2 on 1}[letterpaper, border shrink=5mm]

\usepackage{ifthen}
\newboolean{show_handout_comments}  % Uncomment one of the below
% \setboolean{show_handout_comments}{true}  % Show handout-only comments
\setboolean{show_handout_comments}{false}  % Hide comments

\usepackage{graphicx}
\usepackage{color}
\usepackage{enumerate}
\usepackage{bm}
\usepackage{listings}

\usepackage{booktabs}
\usepackage{multirow}

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{mathtools}
\usepackage{dsfont}
\usepackage{subfigure}

\usetheme{Madrid}
% \usecolortheme{}

\setbeamertemplate{enumerate items}[circle]  % standard enumeration
\setbeamertemplate{itemize items}[circle]  % default itemize
\setbeamertemplate{navigation symbols}{}

% Resuming lists across frames
\newcounter{savedenum}
\newcommand*{\saveenum}{\setcounter{savedenum}{\theenumi}}
\newcommand*{\resume}{\setcounter{enumi}{\thesavedenum}}

% Comments
\newcommand*{\comment}[2][red]{%
  \ifthenelse{\boolean{show_handout_comments}}{
  \only<beamer:0>{\textcolor{#1}{\footnotesize #2}}}{}}

% Boxes
\makeatletter
\newcommand*{\colbox}[2][black]{\textcolor{#1}{%
  \fbox{\normalcolor\m@th$\displaystyle#2$}}}
\makeatother

\newcommand*{\combox}[3][black]{%
  \mbox{\begin{tabular}[t]{@{}c@{}}
    $\colbox[#1]{\displaystyle#2}$\\
    \textcolor{#1}{\scriptsize #3}
    \end{tabular}}}

\newcommand*{\coltextbox}[2][black]{\textcolor{#1}{%
  \setlength{\fboxrule}{1pt}\fbox{\normalcolor#2}}}

\newcommand*{\answerbox}[2][black]{%
  \only<1|handout:0>{#2} \only<2>{\coltextbox[#1]{#2}}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% User-defined LaTeX commands
\DeclareMathOperator*{\Cov}{Cov}
\DeclareMathOperator*{\Var}{Var}
\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}
\DeclarePairedDelimiter{\abs}{\lvert}{\rvert}
\DeclarePairedDelimiter{\norm}{\lVert}{\rVert}
\newcommand*{\ttilde}{{\raise.17ex\hbox{$\scriptstyle\sim$}}}
\newcommand*{\foralls}{\ \forall \ }
\newcommand*{\E}{\mathbb E}
\newcommand*{\R}{\mathbb R}
\newcommand*{\I}{\mathds{1}}
\newcommand*{\Prob}{\mathbb P}
\newcommand*{\notorth}{\ensuremath{\perp\!\!\!\!\!\!\diagup\!\!\!\!\!\!\perp}}
\newcommand*{\orth}{\ensuremath{\perp\!\!\!\perp}}
\newcommand*{\dif}{\,\mathrm{d}}
\newcommand*{\Dif}[1]{\,\mathrm{d^#1}}
\newcommand*{\e}{\mathrm{e}}
\newcommand*{\m}[1]{\textbf{#1}}
\newcommand{\cond}{\;\ifnum\currentgrouptype=16 \middle\fi|\;}
\newcommand*{\bmath}[1]{\boldsymbol{#1}}
\newcommand*{\yestag}{\addtocounter{equation}{1}\tag{\theequation}}
\newcommand*{\notaligned}[1]{\noalign{$\displaystyle #1$}}

\makeatletter
\newsavebox{\mybox}\newsavebox{\mysim}
\newcommand*{\distas}[1]{%
  \savebox{\mybox}{\hbox{\kern3pt$\scriptstyle#1$\kern3pt}}%
  \savebox{\mysim}{\hbox{$\sim$}}%
  \mathbin{\overset{#1}{\kern\z@\resizebox{\wd\mybox}{\ht\mysim}{$\sim$}}}%
}
\makeatother
\newcommand*{\dist}{\sim}
\newcommand*{\distiid}{\distas{\text{i.i.d}}}

\newcommand*{\convas}[1]{\xrightarrow{#1}}
\newcommand*{\conv}{\convas{}}

\makeatletter
\def\moverlay{\mathpalette\mov@rlay}
\def\mov@rlay#1#2{\leavevmode\vtop{%
  \baselineskip\z@skip \lineskiplimit-\maxdimen
  \ialign{\hfil$\m@th#1##$\hfil\cr#2\crcr}}}
\newcommand{\charfusion}[3][\mathord]{
  #1{\ifx#1\mathop\vphantom{#2}\fi\mathpalette\mov@rlay{#2\cr#3}}
  \ifx#1\mathop\expandafter\displaylimits\fi}
\makeatother
\newcommand{\cupdot}{\charfusion[\mathbin]{\cup}{\cdot}}
\newcommand{\bigcupdot}{\charfusion[\mathop]{\bigcup}{\cdot}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\title[601 Final Project]{Hillary Clinton Emails}
\author[Leland Bybee, Roger Fan, Ryan Vaughn]{Leland Bybee, Roger Fan, Ryan Vaughn}
% \institute[]{}
\date{\today}

\begin{document}

\begin{frame}
\maketitle
\end{frame}

\begin{frame}{Some Interesting Topics}

\begin{table}[h]
\centering
\label{topic_top_words}
\scalebox{0.8}{
\begin{tabular}{cccccc}
\hline
Israel & Elections & Libya & Afghanistan & Int. Dev. & Obama \\
\hline
israel & democrat & libya & afghanistan & develop & presid \\
isra & republican & secur & pakistan & state & obama \\
peace & american & travel & afghan & support & said \\
palestinian & polit & libyan & militari & global & hous \\
netanyahu & parti & iraq & general & program & white \\
east & elect & embassi & karzai & effort & administr \\
negoti & obama & attack & offici & intern & polici \\
arab & percent & kill & war & work & aid \\
state & candid & march & forc & includ & advis

\end{tabular}
}
\end{table}

\end{frame}

\begin{frame}{Topic Importance Over Time}

\begin{figure}[h]
\centering
\subfigure[Israel]{\label{fig:t1}\includegraphics[width=29mm]{../images/time_plot6.pdf}}
\subfigure[Elections]{\label{fig:t2}\includegraphics[width=29mm]{../images/time_plot11.pdf}}
\subfigure[Libya]{\label{fig:t3}\includegraphics[width=29mm]{../images/time_plot18.pdf}}
\subfigure[Afghanistan]{\label{fig:t4}\includegraphics[width=29mm]{../images/time_plot27.pdf}}
\subfigure[Int. Dev.]{\label{fig:t5}\includegraphics[width=29mm]{../images/time_plot23.pdf}}
\subfigure[Obama]{\label{fig:t6}\includegraphics[width=29mm]{../images/time_plot25.pdf}}
\label{fig:topic_time_plots}
\end{figure}

\end{frame}

\begin{frame}{Who Says What?}

\begin{table}[h]
\centering
\label{topic_sources}
\scalebox{0.5}{
\begin{tabular}{cccccc}
\hline
Israel & Elections & Libya & Afghanistan & Int. Dev. & Obama \\
\hline
Sidney Blumenthal & SB & Huma Abedin & Judith McHale & JM & SB \\
(SB) & & (HA) & (JM) & & \\
\noalign{\vskip 7mm}
HA & Philippe Reines & Wendy Sherman & HA & Melanne Verveer & PR \\
& (PR) & (WS) & & (MV) & \\
\noalign{\vskip 7mm}
Jake Sullivan & JM & JS & MV & Anne-Marie & Cherly Mills \\
(JS) & & & & Slaughter (AMS) & (CM)\\
\noalign{\vskip 7mm}
AMS & CM & Monica Hanley & JS & CM & HA \\
& & (MH) & & & \\
\noalign{\vskip 7mm}
Hillary Clinton & HA & SB & Richard Verma & JS & HC \\
(HC) & & & (RV) & & \\

\end{tabular}
}
\end{table}

\end{frame}

\begin{frame}

\begin{table}[h]
\centering
\label{multinomial_results}
\scalebox{0.7}{
\begin{tabular}{ccc}
\hline
Source & Success Rate & Testing Observations \\
Hillary Clinton & 0.74 & 849 \\
Philippe Reines & 0.06 & 34 \\
Claire Coleman & 0.52 & 27 \\
Lauren Jiloty & 0.42 & 71 \\
Huma Abedin & 0.36 & 376 \\
Jake Sullivan & 0.23 & 410 \\
Sidney Blumenthal & 0.29 & 87 \\
Cherly Mills & 0.31 & 491 \\
Anne-Marie Slaughter & 0.36 & 42 \\
Monica Hanley & 0.09 & 53 \\
Judith McHale & 0.25 & 28 \\
Robert Russo & 0.00 & 10 \\
Richard Verma & 0.26 & 19 \\
Wendy Sherman & 0.08 & 12 \\
Melanne Verveer & 0.30 & 30 \\
Lona Valmoro & 0.34 & 41
\end{tabular}
}
\end{table}

\end{frame}

\end{document}

### 2016-04-10 code/coherence_scores.R

@@ -59,18 +59,55 @@ genUMassScores <- function(dtm, top_terms, K, term_count, t_ln){
 }
 
 
-scores_mn <- c()
-for(i in seq(5, 70, 5)){
-    load(paste("../data/dtm.rda"))
-    load(paste("../data/model", i, ".rda", sep=""))
-    prob.mat <- exp(model@beta)
-    post.mat <- genPost(prob.mat, dtm)
-    top.terms <- genTopTerms(post.mat, i, 10, Terms(dtm))
-    scores <- genUMassScores(dtm, top.terms, i, 10, dim(dtm)[1])
-    scores_mn <- c(scores_mn, mean(scores))
-    print(i)
+genNullUMass <- function(dtm, samp_n, v_ln, t_ln){
+    # what this does is randomly sample from pairs of
+    # words in the dtm, it then finds the UMass score for
+    # this random pair and returns a vector containing
+    # all these UMass.  This gives a distribution of the
+    # PMIs for the corpus and give us something to compare
+    # the PMI score from UMass with.
+
+    # make dtm truth mat
+    dtm_mat <- as.matrix(dtm)
+    dtm_t <- dtm_mat > 0
+
+    scores <- rep(NA, samp_n)
+    for(i in 1:samp_n){
+        ind <- sample(1:v_ln, 2, replace=TRUE)
+        p_12 <- sum(dtm_t[,ind[1]] & dtm_t[,ind[2]])
+        p_1 <- sum(dtm_t[,ind[1]])
+        p_2 <- sum(dtm_t[,ind[2]])
+        scores[i] <- log((p_12 + 1 / t_ln) * t_ln / (p_2 * p_1))
+    }
+    scores[is.na(scores)] = 0
+    return(scores)
 }
 
 
-ggplot() + geom_line(aes(x=seq(5, 70, 5), y=scores_mn)) + xlab("K") + ylab("Mean UMass Score")    
-ggsave("umass_scores.pdf")
+genUMassScoreTest <- function(umass_scores, K, null_umass_dist){
+    # gets the probability of getting a given score given the UMass score
+    # distribution
+
+    score_prob <- rep(NA, K)
+    for(i in 1:K){
+        score_prob[i] <- sum(umass_scores[i] <= null_umass_dist) / length(null_umass_dist)
+    }
+    return(score_prob)
+}
+
+
+K <- 30
+samp <- 1000
+t_count <- 10
+
[…]

### 2016-04-10 code/word_regression.R

@@ -2,16 +2,17 @@ library(tm)
 library(glmnet)
 library(nnet)
 
-K <- 30
 
-load(paste("../data/model", K, ".rda", sep=""))
+load("../data/dtm.rda")
 load("../data/senders.rda")
 
 people <- table(senders$SenderPerson)
 people <- names(people[people > 100])
 people <- people[people != ""]
 
-data <- data.frame(model@gamma)
+dtm <- weightTfIdf(dtm)
+data <- as.matrix(dtm)
+data <- data.frame(data)
 data$Person <- senders$SenderPerson
 data$Person <- as.factor(data$Person)
 data <- data[data$Person %in% people,]

### 2016-04-10 code/dtm.R
Minor changes.

@@ -4,12 +4,10 @@ library(SnowballC)
 
 tab = read.csv("../data/emails.csv")
 ids = data.frame(Id=1:nrow(tab))
-senders = tab[c('SenderPerson', 'SenderPersonId')]
 ids_kept = 1:nrow(tab)
 date = as.Date(tab$DateSent)
 
 tab = tab[!is.na(date),]
-senders = senders[!is.na(date),]
 ids_kept = ids_kept[!is.na(date)]
 date = date[!is.na(date)]
 
@@ -18,6 +16,7 @@ corpus = Corpus(vect)
 corpus = tm_map(corpus, content_transformer(tolower))
 corpus = tm_map(corpus, removePunctuation)
 corpus = tm_map(corpus, removeNumbers)
+# corpus = tm_map(corpus, removeWords, c(stopwords("english"), 'fyi'))
 corpus = tm_map(corpus, removeWords, stopwords("english"))
 corpus = tm_map(corpus, stemDocument)
 corpus = tm_map(corpus, stripWhitespace)
@@ -28,7 +27,6 @@ dtm = removeSparseTerms(dtm, 0.999)
 totals = apply(dtm, 1, sum)
 dtm = dtm[totals > 0,]
 dates = date[totals > 0]
-senders = senders[totals > 0,]
 ids_kept = ids_kept[totals>0]
 
 ids_kept = data.frame(Id=ids_kept, kept=1)
@@ -36,6 +34,5 @@ ids = merge(ids, ids_kept, by='Id', all.x=TRUE)
 ids$kept[is.na(ids$kept)] = 0
 
 save(ids, file="../data/ids_kept.rda")
-save(senders, file="../data/senders.rda")
 save(dates, file="../data/dates.rda")
 save(dtm, file="../data/dtm.rda")

### 2016-04-10 presentation/presentation.tex
add multinomial regression title

@@
 \usepackage{subfigure}
+\usepackage{tikz}
+\usetikzlibrary{bayesnet}
 
@@
 
+\begin{frame}{Latent Dirichlet Allocation}
+
+\begin{figure}
+\centering
+\begin{tikzpicture}
+\tikzstyle{main}=[circle, minimum size = 10mm, thick, draw =black!80, node distance = 16mm]
+\tikzstyle{connect}=[-latex, thick]
+\tikzstyle{box}=[rectangle, draw=black!100]
+  \node[main, fill = white!100] (alpha) [label=below:$\alpha$] { };
+  \node[main] (theta) [right=of alpha,label=below:$\theta$] { };
+  \node[main] (z) [right=of theta,label=below:z] {};
+  \node[main] (beta) [above=of z,label=below:$\beta$] { };
+  \node[main, fill = black!10] (w) [right=of z,label=below:w] { };
+  \path (alpha) edge [connect] (theta)
+        (theta) edge [connect] (z)
+        (z) edge [connect] (w)
+        (beta) edge [connect] (w);
+  \node[rectangle, inner sep=0mm, fit= (z) (w),label=below right:N, xshift=13mm] {};
+  \node[rectangle, inner sep=4.4mm,draw=black!100, fit= (z) (w)] {};
+  \node[rectangle, inner sep=4.6mm, fit= (z) (w),label=below right:M, xshift=12.5mm] {};
+  \node[rectangle, inner sep=9mm, draw=black!100, fit = (theta) (z) (w)] {};
+\end{tikzpicture}
+\end{figure}
+
+\end{frame}
+
+\begin{frame}{Latent Dirichlet Allocation: Some Details}
+
+\begin{itemize}
+\item We use $K = 30$ topics for our resulting model.
+\item What we ultimately care about are $\theta$ and $\beta$.
+\item $\theta$ corresponds to how likely a topic is to appear in a document.
+\item $\beta$ corresponds to how likely each word is to be associated with each topic.
+\end{itemize}
+
+\end{frame}
+
+\begin{frame}{Latent Dirichlet Allocation: Some Details}
+
+\begin{itemize}
+\item Some questions we want to answer with LDA
+\begin{itemize}
+\item Can we see sensible topics in the LDA output?
+\item Who is associated most with each issue?
+\item Do the topics proportions for each email line up with real world events?
+\item Can we predict the source of a given email?
+\end{itemize}
+\end{itemize}
+
+\end{frame}
+
 \begin{frame}{Some Interesting Topics}
@@
 
-\begin{frame}
+\begin{frame}{Multinomial Logistic Regression}
+
+\begin{itemize}
+\item We next want to ask can we predict who said what?
+\item To answer this question we employ multinomial regression.
+\item We take a subset of people who sent emails, only those who have more that 100 emails sent and try prediction for these.
+\end{itemize}
+
+\end{frame}
+
+\begin{frame}{Multinomial Logistic Regression Results}
 

### 2016-04-10 code/mds.R
MDS and clustering.

@@ -1,0 +1,17 @@
+library(tm)
+library(SnowballC)
+
+load("../data/dtm.rda")
+datatf = weightTf(dtm)
+mat = as.matrix(datatf)
+write.table(mat, '../data/dtm_tf.csv', row.names=FALSE, col.names=FALSE)
+
+datatfidf = weightTfIdf(dtm)
+mat = as.matrix(datatfidf)
+write.table(mat, '../data/dtm_tfidf.csv', row.names=FALSE, col.names=FALSE)
+
+
+load("../data/senders.rda")
+load("../data/ids_kept.rda")
+write.csv(senders, '../data/senders.csv', row.names=FALSE)
+write.csv(ids, '../data/ids_kept.csv', row.names=FALSE)

### 2016-04-10 code/mds.py

@@ -1,0 +1,132 @@
+from time import time
+
+import numpy as np
+import numpy.linalg as la
+from scipy import sparse
+from scipy.sparse.linalg import eigsh
+import pandas as pd
+import matplotlib.pyplot as plt
+from matplotlib import cm
+from mpl_toolkits.mplot3d import Axes3D
+from sklearn.metrics import pairwise_distances
+from sklearn.preprocessing import normalize
+from sklearn.cluster import SpectralClustering
+
+def save_sparse_csr(filename, array):
+    np.savez(filename, data=array.data, indices=array.indices,
+             indptr=array.indptr, shape=array.shape)
+
+def load_sparse_csr(filename):
+    with np.load(filename) as loader:
+        res = sparse.csr_matrix((
+            loader['data'], loader['indices'], loader['indptr']),
+            shape=loader['shape'])
+    return res
+
+
+# data = np.loadtxt('../data/dtm_tfidf.csv')
+
+# sdata = sparse.csr_matrix(data)
+# save_sparse_csr('../data/sdtm_tfidf.npz', sdata)
+
+
+# data = np.loadtxt('../data/dtm_tf.csv')
+
+# sdata = sparse.csr_matrix(data)
+# save_sparse_csr('../data/sdtm_tf.npz', sdata)
+
+
+keep = pd.read_csv('../data/ids_kept.csv')
+keep = keep['kept'].astype(bool)
+
+emails = pd.read_csv('../data/emails.csv')
+emails = emails.reset_index()
+emails = emails.ix[keep]
+emails = emails.reset_index()
+hill = np.array(emails['SenderPersonId'] == 80)
+
+# sdata = load_sparse_csr('../data/sdtm_tfidf.npz')
+sdata = load_sparse_csr('../data/sdtm_tf.npz')
+
+
+np.random.seed(2634)
+inds = np.random.choice(sdata.shape[0], 8000, replace=False)
+sd = sdata[inds]
+hill = hill[inds]
+
+
+dist = pairwise_distances(sd, metric='cosine')
+dist[dist < 0.] = 0.
+dist2 = dist**2
+
+n = dist2.shape[0]
+H = (np.eye(n) - np.ones((n, n))/n)
+G = -(1/2) * H @ dist2 @ H
+
+eig = eigsh(G, k=3)
[…]

### 2016-04-12 presentation/presentation.tex
Added data and MDS/clustering to presentation.

@@
-% \documentclass[14pt]{beamer}
-\documentclass[handout,14pt]{beamer}
+% \documentclass[13pt]{beamer}
+\documentclass[handout,13pt]{beamer}
 
@@
 \usetheme{Madrid}
-% \usecolortheme{}
+\usecolortheme{beaver}
 
@@
 
+\begin{frame}{Data}
+\begin{itemize}
+\item From 2008 to 2013, Hillary Clinton and some of her staff used a private email server for much of their communication
+\item In response to FOIA requests, the State Department has released pdfs of roughly 30,000 of these emails, with roughly 8,000 sent by Clinton
+\item We have a dataset of all these released emails, including sender and receiver information\footnote{Thanks to Ben Hamner and the WSJ for making their code and data available, respectively.}
+\pause\item Bag-of-words model
+  \begin{itemize}
+  \item Stemming: combining words with the same ``root''
+  \item Remove extremely rare words and extremely common (stop) words
+  \end{itemize}
+\item After cleaning, roughly 28,000 emails and a total vocabulary of over 3,000 words
+\end{itemize}
+\end{frame}
+
+\begin{frame}{Visualization}
+\begin{itemize}
+\item In order to visualize these emails, we first need a measure of distance
+\item Cosine similarity:
+  \begin{equation*}
+  \cos(\phi) = \frac{<V, W>}{\norm{V}\norm{W}}
+  \end{equation*}
+\item We can then use classical multi-dimensional scaling to visualize this data in lower dimensions
+\end{itemize}
+\end{frame}
+
+\begin{frame}{Visualization}
+\begin{figure}[h]
+\centering
+\subfigure[2D]{\label{fig:mds_2d}\includegraphics[width=0.44\linewidth]{../images/mds_2d.pdf}}
+\subfigure[3D]{\label{fig:mds_3d}\includegraphics[width=0.54\linewidth]{../images/mds_3d_1.pdf}}
+\label{fig:mds}
+\end{figure}
+\end{frame}
+
+\begin{frame}{Spectral Clustering}
+\begin{itemize}
+\item Cluster points using their pairwise similarity
+\item Computer the first $K$ eigenvectors of the normalized Laplacian
+  \begin{equation*}
+  L = I - D^{-1/2} S D^{-1/2}
+  \end{equation*}
+\item Perform $k$-means clustering on the resulting eigenvectors
+\end{itemize}
+\end{frame}
+
+\begin{frame}{Spectral Clustering}
+\begin{figure}[h]
+\centering
+\subfigure[2D]{\label{fig:cluster_2d}\includegraphics[width=0.44\linewidth]{../images/mds_2d_cluster.pdf}}
+\subfigure[3D]{\label{fig:cluster_3d}\includegraphics[width=0.54\linewidth]{../images/mds_3d_cluster_1.pdf}}
+\label{fig:cluster}
+\end{figure}
+\end{frame}
+
 \begin{frame}{Latent Dirichlet Allocation}
-
 \begin{figure}
 \centering
-\begin{tikzpicture}
+\begin{tikzpicture}[scale=1.0, every node/.style={transform shape}]
 \tikzstyle{main}=[circle, minimum size = 10mm, thick, draw =black!80, node distance = 16mm]
@@
 \tikzstyle{box}=[rectangle, draw=black!100]
-  \node[main, fill = white!100] (alpha) [label=below:$\alpha$] { };
-  \node[main] (theta) [right=of alpha,label=below:$\theta$] { };
-  \node[main] (z) [right=of theta,label=below:z] {};
-  \node[main] (beta) [above=of z,label=below:$\beta$] { };
-  \node[main, fill = black!10] (w) [right=of z,label=below:w] { };
-  \path (alpha) edge [connect] (theta)
-        (theta) edge [connect] (z)
-        (z) edge [connect] (w)
-        (beta) edge [connect] (w);
-  \node[rectangle, inner sep=0mm, fit= (z) (w),label=below right:N, xshift=13mm] {};
-  \node[rectangle, inner sep=4.4mm,draw=black!100, fit= (z) (w)] {};
-  \node[rectangle, inner sep=4.6mm, fit= (z) (w),label=below right:M, xshift=12.5mm] {};
-  \node[rectangle, inner sep=9mm, draw=black!100, fit = (theta) (z) (w)] {};
+  \node[main] (alpha) {$\alpha$};
+  \node[main] (theta) [right=of alpha] {$\theta$};
+  \node[main] (z) [right=of theta] {$z$};
+  \node[main] (beta) [above=of z] {$\beta$};
+  \node[main, fill=black!10] (w) [right=of z] {$w$};
+  \edge {alpha} {theta};
+  \edge {theta} {z};
+  \edge {z,beta} {w};
+  \plate {words} {(z)(w)} {$N_m$};
+  \plate {docs} {(theta)(z)(w)(words.south east)(words.north west)} {$M$};
 \end{tikzpicture}
 \end{figure}
-
 \end{frame}
@@
 \begin{frame}{Latent Dirichlet Allocation: Some Details}
-
 \begin{itemize}
@@
 \end{itemize}
-
 \end{frame}
@@
 \begin{frame}{Some Interesting Topics}
-
 \begin{table}[h]
@@
 \begin{tabular}{cccccc}
-\hline
+\toprule
 Israel & Elections & Libya & Afghanistan & Int. Dev. & Obama \\
-\hline
+\midrule
 israel & democrat & libya & afghanistan & develop & presid \\
@@
 arab & percent & kill & war & work & aid \\
-state & candid & march & forc & includ & advis
-
+state & candid & march & forc & includ & advis \\
+\bottomrule
 \end{tabular}
@@
 \end{table}
-
 \end{frame}
@@
 \begin{frame}{Topic Importance Over Time}
-
 \begin{figure}[h]
 \centering
-\subfigure[Israel]{\label{fig:t1}\includegraphics[width=29mm]{../images/time_plot6.pdf}}
-\subfigure[Elections]{\label{fig:t2}\includegraphics[width=29mm]{../images/time_plot11.pdf}}
-\subfigure[Libya]{\label{fig:t3}\includegraphics[width=29mm]{../images/time_plot18.pdf}}
-\subfigure[Afghanistan]{\label{fig:t4}\includegraphics[width=29mm]{../images/time_plot27.pdf}}
-\subfigure[Int. Dev.]{\label{fig:t5}\includegraphics[width=29mm]{../images/time_plot23.pdf}}
-\subfigure[Obama]{\label{fig:t6}\includegraphics[width=29mm]{../images/time_plot25.pdf}}
+\subfigure[Israel]{\label{fig:t1}\includegraphics[width=0.25\linewidth]{../images/time_plot6.pdf}}
+\subfigure[Elections]{\label{fig:t2}\includegraphics[width=0.25\linewidth]{../images/time_plot11.pdf}}
+\subfigure[Libya]{\label{fig:t3}\includegraphics[width=0.25\linewidth]{../images/time_plot18.pdf}}
+\subfigure[Afghanistan]{\label{fig:t4}\includegraphics[width=0.25\linewidth]{../images/time_plot27.pdf}}
+\subfigure[Int. Dev.]{\label{fig:t5}\includegraphics[width=0.25\linewidth]{../images/time_plot23.pdf}}
+\subfigure[Obama]{\label{fig:t6}\includegraphics[width=0.25\linewidth]{../images/time_plot25.pdf}}
 \label{fig:topic_time_plots}
 \end{figure}
-
 \end{frame}
@@
 \begin{frame}{Who Says What?}
-
 \begin{table}[h]
@@
 \label{topic_sources}
-\scalebox{0.5}{
+\scalebox{0.58}{
 \begin{tabular}{cccccc}
-\hline
+\toprule
 Israel & Elections & Libya & Afghanistan & Int. Dev. & Obama \\
-\hline
+\midrule
 Sidney Blumenthal & SB & Huma Abedin & Judith McHale & JM & SB \\
@@
 (HC) & & & (RV) & & \\
-
+\bottomrule
 \end{tabular}
@@
 \begin{frame}{Multinomial Logistic Regression}
-
 \begin{itemize}
@@
 \begin{frame}{Multinomial Logistic Regression Results}
-
 \begin{table}[h]
@@
 \begin{tabular}{ccc}
-\hline
+\toprule
 Source & Success Rate & Testing Observations \\
+\midrule
 Hillary Clinton & 0.74 & 849 \\
@@
 Melanne Verveer & 0.30 & 30 \\
-Lona Valmoro & 0.34 & 41
+Lona Valmoro & 0.34 & 41 \\
+\bottomrule
 \end{tabular}

### 2016-04-12 code/mds.py

@@ -84,12 +84,26 @@ colors = cm.Paired(np.linspace(0, 1, 10))
 
 fig = plt.figure()
 ax = fig.add_subplot(111)
+ax.scatter(z1, z2, s=10, lw=0.2)
+fig.savefig('../images/mds_2d.pdf')
+
+fig = plt.figure()
+ax = fig.add_subplot(111)
 for g, c in zip(range(10), colors):
     ax.scatter(z1[y_pred==g], z2[y_pred==g],
                c=c, s=10, lw=0.2, label=str(g))
 ax.legend(scatterpoints=1, markerscale=2)
-fig.savefig('../mds_2d.pdf')
+fig.savefig('../images/mds_2d_cluster.pdf')
 
+
+fig = plt.figure()
+ax = fig.add_subplot(111, projection='3d')
+ax.scatter(z1, z2, z3, s=10, lw=0.2)
+ax.view_init(29, 46)
+fig.savefig('../images/mds_3d_1.pdf')
+
+ax.view_init(-10, 227)
+fig.savefig('../images/mds_3d_2.pdf')
 
 fig = plt.figure()
 ax = fig.add_subplot(111, projection='3d')
@@ -98,10 +112,10 @@ for g, c in zip(range(10), colors):
                c=c, s=10, lw=0.2, label=str(g))
 ax.legend(scatterpoints=1, markerscale=2)
 ax.view_init(29, 46)
-fig.savefig('../mds_3d_1.pdf')
+fig.savefig('../images/mds_3d_cluster_1.pdf')
 
 ax.view_init(-10, 227)
-fig.savefig('../mds_3d_2.pdf')
+fig.savefig('../images/mds_3d_cluster_2.pdf')
 
 
 np.savetxt('../data/clusters.txt', np.column_stack((inds, y_pred)))

### 2016-04-13 presentation/presentation.tex
Updating presentation.

@@
 \item In response to FOIA requests, the State Department has released pdfs of roughly 30,000 of these emails, with roughly 8,000 sent by Clinton
+\item We mostly want to condense and explore the data
+  \begin{itemize}
+  \item Break down a huge interpretation problem to a human-sized one
+  \item Find specific and relatable observations, not just statistical ones
+  \end{itemize}
+\end{itemize}
+\end{frame}
+
+\begin{frame}{Data}
+\begin{itemize}
 \item We have a dataset of all these released emails, including sender and receiver information\footnote{Thanks to Ben Hamner and the WSJ for making their code and data available, respectively.}
@@
 \item Can we see sensible topics in the LDA output?
+\item What are the most common topics of the emails?
 \item Who is associated most with each issue?
@@
 \end{itemize}
+\end{frame}
+
+\begin{frame}{Exploring Topics}
+\begin{figure}[h]
+\centering
+\includegraphics[width=0.99\linewidth]{../images/topic_words.pdf}
+\label{fig:topics}
+\end{figure}
+\end{frame}
+
+\begin{frame}{Primary Topic Frequency}
+\begin{columns}
+
+  \column{.7\textwidth}
+  \begin{figure}[h]
+  \centering
+  \includegraphics[width=0.8\linewidth]{../images/topic_desc.png}
+  \label{fig:topics_desc}
+  \end{figure}
+
+  \column{.3\textwidth}
+  \begin{figure}[h]
+  \centering
+  \includegraphics[height=0.75\textheight]{../images/topic_freq.png}
+  \label{fig:topics_freq}
+  \end{figure}
+
+\end{columns}
+\end{frame}
+
+\begin{frame}{Some ``Not'' Interesting Topics}
+\begin{table}[h]
+\centering
+\label{topic_common_words}
+\scalebox{0.8}{
+\begin{tabular}{cccccc}
+\toprule
+Common 1 & Common 2 & Common 3 & Logistics & Meeting & Communication \\
+\midrule
+know & think & will & secretari & meet & call \\
+just & like & work & depart & reuters & huma \\
+want & good & week & office & follow & abedin \\
+let & say & need & room & update & schedul \\
+ask & dont & next & state & list & sheet \\
+come & look & also & arriv & happi & request \\
+tri & got & plan & rout & monday & speak \\
+sure & tell & start & privat & schedule & readout \\
+thx & thing & issu & office & set & calls \\
+\bottomrule
+\end{tabular}
+}
+\end{table}
 \end{frame}
@@
 
-\begin{frame}{Multinomial Logistic Regression}
+% \begin{frame}{Multinomial Logistic Regression}
+% \begin{itemize}
+% \item We next want to ask can we predict who said what?
+% \item To answer this question we employ multinomial regression.
+% \item We take a subset of people who sent emails, only those who have more that 100 emails sent and try prediction for these.
+% \end{itemize}
+% \end{frame}
+
+% \begin{frame}{Multinomial Logistic Regression Results}
+% \begin{table}[h]
+% \centering
+% \label{multinomial_results}
+% \scalebox{0.7}{
+% \begin{tabular}{ccc}
+% \toprule
+% Source & Success Rate & Testing Observations \\
+% \midrule
+% Hillary Clinton & 0.74 & 849 \\
+% Philippe Reines & 0.06 & 34 \\
+% Claire Coleman & 0.52 & 27 \\
+% Lauren Jiloty & 0.42 & 71 \\
+% Huma Abedin & 0.36 & 376 \\
+% Jake Sullivan & 0.23 & 410 \\
+% Sidney Blumenthal & 0.29 & 87 \\
+% Cherly Mills & 0.31 & 491 \\
+% Anne-Marie Slaughter & 0.36 & 42 \\
+% Monica Hanley & 0.09 & 53 \\
+% Judith McHale & 0.25 & 28 \\
+% Robert Russo & 0.00 & 10 \\
+% Richard Verma & 0.26 & 19 \\
+% Wendy Sherman & 0.08 & 12 \\
+% Melanne Verveer & 0.30 & 30 \\
+% Lona Valmoro & 0.34 & 41 \\
+% \bottomrule
+% \end{tabular}
+% }
+% \end{table}
+% \end{frame}
+
+\begin{frame}{Conclusion}
 \begin{itemize}
-\item We next want to ask can we predict who said what?
-\item To answer this question we employ multinomial regression.
-\item We take a subset of people who sent emails, only those who have more that 100 emails sent and try prediction for these.
+\item We've broken the corpus down to a level where we can effectively analyze it and draw conclusions using both human and statistical analysis
+\item This has only been a sample of the many questions we could address using the LDA output
+\item Possible future directions
+  \begin{itemize}
+  \item Some emails are redacted, how do email topics relate to this
+  \item Correlation between topics, what topics appear together
+  \item Predicting senders or receivers based on email text
+  \end{itemize}
 \end{itemize}
@@
 
-\begin{frame}{Multinomial Logistic Regression Results}
-\begin{table}[h]
-\centering
-\label{multinomial_results}
-\scalebox{0.7}{
-\begin{tabular}{ccc}
-\toprule
-Source & Success Rate & Testing Observations \\
-\midrule
-Hillary Clinton & 0.74 & 849 \\
-Philippe Reines & 0.06 & 34 \\
-Claire Coleman & 0.52 & 27 \\
-Lauren Jiloty & 0.42 & 71 \\
-Huma Abedin & 0.36 & 376 \\
-Jake Sullivan & 0.23 & 410 \\
-Sidney Blumenthal & 0.29 & 87 \\
-Cherly Mills & 0.31 & 491 \\
-Anne-Marie Slaughter & 0.36 & 42 \\
-Monica Hanley & 0.09 & 53 \\
-Judith McHale & 0.25 & 28 \\
-Robert Russo & 0.00 & 10 \\
-Richard Verma & 0.26 & 19 \\
-Wendy Sherman & 0.08 & 12 \\
-Melanne Verveer & 0.30 & 30 \\
-Lona Valmoro & 0.34 & 41 \\
-\bottomrule
-\end{tabular}
-}
-\end{table}
-\end{frame}
-
 \end{document}

### 2016-04-13 paper/paper.tex
add paper outline

\documentclass{article}

\begin{document}

\section{Introduction}

\section{Data Summary}

\section{MDS}

\section{Spectral Clustering}

\section{TM Background/Estimation}

\section{Interpreting Topics/Model Selection}

\section{Types of Topics}

\section{Interesting Topics}

\section{Who Says What/Multinomial Regression}

\section{Conclusion}

\end{document}

### 2016-04-13 code/topic_regression.R

@@ -6,6 +6,7 @@ K <- 30
 
 load(paste("../data/model", K, ".rda", sep=""))
 load("../data/senders.rda")
+clusters <- read.table("../data/clusters.txt", header=FALSE)
 
 people <- table(senders$SenderPerson)
 people <- names(people[people > 100])

### 2016-04-14 presentation/presentation.tex
Minor changes.
add multinomial regression

--- 2016-04-12 presentation/presentation.tex
@@
 
+\begin{frame}{Conclusion}
+\begin{itemize}
+\item We've broken the corpus down to a level where we can effectively analyze it and draw conclusions using both human and statistical analysis
+\item This has only been a sample of the many questions we could address using the LDA output
+\item Possible future directions
+  \begin{itemize}
+  \item Some emails are redacted, how do email topics relate to this
+  \item Correlation between topics, what topics appear together
+  \item Predicting senders or receivers based on email text
+  \end{itemize}
+\end{itemize}
+\end{frame}
+
 \end{document}

### 2016-04-14 presentation/presentation.tex
add beginnings of code to make coefficient matrix

@@
 \item What are the most common topics of the emails?
-\item Who is associated most with each issue?
-\item Do the topics proportions for each email line up with real world events?
-\item Can we predict the source of a given email?
+\item Do the topics for each email line up with real world events?
+\item Can we associate email senders with topics?
 \end{itemize}
@@
 \begin{itemize}
-\item We next want to ask can we predict who said what?
+\item Can we do a better job associating email senders with topics?
 \item To answer this question we employ multinomial regression.
-\item We take a subset of people who sent emails, only those who have more that 100 emails sent and try prediction for these.
+\item We take a subset of people who sent emails, only those who have more that 100 emails sent and try to predict the sender using the topics.
 \end{itemize}
@@
   \item Correlation between topics, what topics appear together
-  \item Predicting senders or receivers based on email text
+  \item Incorporating information on receivers 
   \end{itemize}
+\item If this data intrigues you, all the code we used to download, process, and analyze the data is (will be) available at \url{https://github.com/lbybee/601_Final_Project}.
 \end{itemize}

### 2016-04-14 code/topic_regression.R

@@ -1,12 +1,13 @@
 library(tm)
 library(glmnet)
 library(nnet)
+library(ggplot2)
+library(reshape2)
 
 K <- 30
 
 load(paste("../data/model", K, ".rda", sep=""))
 load("../data/senders.rda")
-clusters <- read.table("../data/clusters.txt", header=FALSE)
 
 people <- table(senders$SenderPerson)
 people <- names(people[people > 100])
@@ -41,3 +42,14 @@ for(i in u_names){
     count <- c(count, sum(sub_ind))
     failure <- c(failure, sum(test_pred_names[sub_ind] != test_names[sub_ind]))
 }
+
+coefficients <- data.frame(coef(fit))
+coefficients <- coefficients[,2:(K+1)]
+coefficients[coefficients < 0] <- 0
+#coefficients <- scale(coefficients)
+for(i in 1:K){
+    coefficients[,i] <- (coefficients[,i] - min(coefficients[,i])) / (max(coefficients[,i]) - min(coefficients[,i]) + 0.0000001)
+}
+mlt <- melt(t(coefficients))
+ggplot(data=mlt) + geom_tile(aes(x=Var1, y=Var2, fill=value))
+ggsave("coefficients.pdf")

### 2016-04-14 code/topic_regression.R
add coefficient

@@ -13,7 +13,8 @@ people <- table(senders$SenderPerson)
 people <- names(people[people > 100])
 people <- people[people != ""]
 
-data <- data.frame(model@gamma)
+temp <- scale(model@gamma)
+data <- data.frame(temp)
 data$Person <- senders$SenderPerson
 data$Person <- as.factor(data$Person)
 data <- data[data$Person %in% people,]
@@ -50,6 +51,7 @@ coefficients[coefficients < 0] <- 0
 for(i in 1:K){
     coefficients[,i] <- (coefficients[,i] - min(coefficients[,i])) / (max(coefficients[,i]) - min(coefficients[,i]) + 0.0000001)
 }
-mlt <- melt(t(coefficients))
-ggplot(data=mlt) + geom_tile(aes(x=Var1, y=Var2, fill=value))
+mlt <- melt(t(t(coefficients)))
+colnames(mlt) <- c("Sender", "Topic", "value")
+ggplot(data=mlt) + geom_tile(aes(x=Topic, y=Sender, fill=value)) + theme(legend.position = "none", axis.text.x = element_text(angle = 90, hjust = 0))
 ggsave("coefficients.pdf")

### 2016-04-15 code/topic_regression.R
update coefficient plot

@@ -3,6 +3,8 @@ library(glmnet)
 library(nnet)
 library(ggplot2)
 library(reshape2)
+library(RColorBrewer)
+require(extrafont)
 
 K <- 30
 
@@ -13,6 +15,8 @@ people <- table(senders$SenderPerson)
 people <- names(people[people > 100])
 people <- people[people != ""]
 
+#temp <- model@gamma
+#temp <- sweep(model@gamma, 2, apply(model@gamma, 2, mean))
 temp <- scale(model@gamma)
 data <- data.frame(temp)
 data$Person <- senders$SenderPerson
@@ -46,12 +50,23 @@ for(i in u_names){
 
 coefficients <- data.frame(coef(fit))
 coefficients <- coefficients[,2:(K+1)]
-coefficients[coefficients < 0] <- 0
+#coefficients[coefficients < -1] <- -1
+#coefficients[coefficients < 0] <- 0
 #coefficients <- scale(coefficients)
-for(i in 1:K){
-    coefficients[,i] <- (coefficients[,i] - min(coefficients[,i])) / (max(coefficients[,i]) - min(coefficients[,i]) + 0.0000001)
-}
+#for(i in 1:K){
+#    coefficients[,i] <- (coefficients[,i] - min(coefficients[,i])) / (max(coefficients[,i]) - min(coefficients[,i]) + 0.0000001) 
+#}
+test <- c("Meetings", "Middle East", "Staff", "Politics", "Terrorism", "Foreign Policy", "Press", "Hillary", "Communication", "Common")
+col <- c('#e31a1c','#1f78b4','#a6cee3','#33a02c','#b2df8a','#fb9a99','#ff7f00','#6a3d9a','#cab2d6','#fdbf6f')
+sortorder <- c(5, 22, 6, 18, 19, 27, 29, 2, 7, 13, 21, 23, 26, 11, 17, 25, 16, 20, 4, 12, 9, 10, 24, 28, 30, 1, 3, 8, 14, 15)
+colororder <- c(rep(col[5], 2), rep(col[2], 5), rep(col[6], 6), rep(col[4], 3), rep(col[3], 2), rep(col[7], 1), rep(col[8], 1), rep(col[1], 5), rep(col[9], 1), rep(col[10], 4))
+coefficients <- coefficients[,sortorder]
+coefficients[coefficients < -0.9] <- -0.9
+coefficients[coefficients > 0.9] <- 0.9 
 mlt <- melt(t(t(coefficients)))
[…]

### 2016-04-15 code/topic_regression.R
return to PiGn color scheme (brewer says the colorblind can see it) and scale coefficients properly

@@ -15,9 +15,9 @@ people <- table(senders$SenderPerson)
 people <- names(people[people > 100])
 people <- people[people != ""]
 
-#temp <- model@gamma
+temp <- model@gamma
 #temp <- sweep(model@gamma, 2, apply(model@gamma, 2, mean))
-temp <- scale(model@gamma)
+#temp <- scale(model@gamma)
 data <- data.frame(temp)
 data$Person <- senders$SenderPerson
 data$Person <- as.factor(data$Person)
@@ -52,21 +52,22 @@ coefficients <- data.frame(coef(fit))
 coefficients <- coefficients[,2:(K+1)]
 #coefficients[coefficients < -1] <- -1
 #coefficients[coefficients < 0] <- 0
-#coefficients <- scale(coefficients)
+coefficients <- scale(coefficients)
 #for(i in 1:K){
-#    coefficients[,i] <- (coefficients[,i] - min(coefficients[,i])) / (max(coefficients[,i]) - min(coefficients[,i]) + 0.0000001) 
+#    coefficients[,i] <- (coefficients[,i] - min(coefficients[,i])) / (max(coefficients[,i]) - min(coefficients[,i]) + 0.0000001)
 #}
+#coefficients <- coefficients - mean(as.matrix(coefficients))
 test <- c("Meetings", "Middle East", "Staff", "Politics", "Terrorism", "Foreign Policy", "Press", "Hillary", "Communication", "Common")
 col <- c('#e31a1c','#1f78b4','#a6cee3','#33a02c','#b2df8a','#fb9a99','#ff7f00','#6a3d9a','#cab2d6','#fdbf6f')
 sortorder <- c(5, 22, 6, 18, 19, 27, 29, 2, 7, 13, 21, 23, 26, 11, 17, 25, 16, 20, 4, 12, 9, 10, 24, 28, 30, 1, 3, 8, 14, 15)
 colororder <- c(rep(col[5], 2), rep(col[2], 5), rep(col[6], 6), rep(col[4], 3), rep(col[3], 2), rep(col[7], 1), rep(col[8], 1), rep(col[1], 5), rep(col[9], 1), rep(col[10], 4))
 coefficients <- coefficients[,sortorder]
-coefficients[coefficients < -0.9] <- -0.9
-coefficients[coefficients > 0.9] <- 0.9 
+coefficients[coefficients < -2] <- -2 
+coefficients[coefficients > 2] <- 2 
 mlt <- melt(t(t(coefficients)))
[…]

### 2016-04-18 code/mds.py
Redoing mds images, saving as png.

@@ -84,38 +84,44 @@ colors = cm.Paired(np.linspace(0, 1, 10))
 
 fig = plt.figure()
 ax = fig.add_subplot(111)
-ax.scatter(z1, z2, s=10, lw=0.2)
-fig.savefig('../images/mds_2d.pdf')
+ax.scatter(z1, z2, s=10, lw=0.15)
+fig.savefig('../images/mds_2d.pdf', bbox_inches='tight')
+fig.savefig('../images/mds_2d.png', bbox_inches='tight', dpi=900)
 
 fig = plt.figure()
 ax = fig.add_subplot(111)
 for g, c in zip(range(10), colors):
     ax.scatter(z1[y_pred==g], z2[y_pred==g],
-               c=c, s=10, lw=0.2, label=str(g))
+               c=c, s=10, lw=0.15, label=str(g))
 ax.legend(scatterpoints=1, markerscale=2)
-fig.savefig('../images/mds_2d_cluster.pdf')
+fig.savefig('../images/mds_2d_cluster.pdf', bbox_inches='tight')
+fig.savefig('../images/mds_2d_cluster.png', bbox_inches='tight', dpi=900)
 
 
 fig = plt.figure()
 ax = fig.add_subplot(111, projection='3d')
-ax.scatter(z1, z2, z3, s=10, lw=0.2)
+ax.scatter(z1, z2, z3, s=10, lw=0.15)
 ax.view_init(29, 46)
-fig.savefig('../images/mds_3d_1.pdf')
+fig.savefig('../images/mds_3d_1.pdf', bbox_inches='tight')
+fig.savefig('../images/mds_3d_1.png', bbox_inches='tight', dpi=900)
 
 ax.view_init(-10, 227)
-fig.savefig('../images/mds_3d_2.pdf')
+fig.savefig('../images/mds_3d_2.pdf', bbox_inches='tight')
+fig.savefig('../images/mds_3d_2.png', bbox_inches='tight', dpi=900)
 
 fig = plt.figure()
 ax = fig.add_subplot(111, projection='3d')
 for g, c in zip(range(10), colors):
     ax.scatter(z1[y_pred==g], z2[y_pred==g], z3[y_pred==g],
-               c=c, s=10, lw=0.2, label=str(g))
+               c=c, s=10, lw=0.15, label=str(g))
 ax.legend(scatterpoints=1, markerscale=2)
 ax.view_init(29, 46)
[…]

### 2016-04-18 paper/paper.tex
Fleshing out paper outline.

@@
-\documentclass{article}
+\documentclass[12pt]{article}
+
+% General
+\usepackage[round]{natbib}
+\usepackage{setspace}
+\usepackage{geometry}
+\usepackage[section]{placeins}
+\usepackage[hidelinks]{hyperref}
+\usepackage{graphicx}
+\usepackage{color}
+\usepackage{titlesec}
+\usepackage[page]{appendix}
+\usepackage{enumerate}
+
+% Tables/Figures
+\usepackage{lscape}
+\usepackage{booktabs}
+\usepackage{rotating}
+\usepackage{multirow}
+\usepackage{longtable}
+\usepackage{caption}
+\usepackage{subcaption}
+\usepackage{float}
+
+% Math
+\usepackage{amsmath}
+\usepackage{amssymb}
+\usepackage{amsthm}
+\usepackage{mathtools}
+\usepackage{dsfont}
+
+% \doublespacing
+\onehalfspacing
+% \singlespacing
+
+% \numberwithin{equation}{section}
+
+\geometry{paper=letterpaper, margin=1in}
+\captionsetup{font=small}
+
+% Code
+\usepackage{textcomp}
+\usepackage{sourcecodepro}
+\usepackage{listings}
+\definecolor{commentgrey}{gray}{0.45}
+\definecolor{backgray}{gray}{0.96}
+\lstset{
+  basicstyle=\footnotesize\ttfamily, keywordstyle=\footnotesize,
+  backgroundcolor=\color{backgray}, commentstyle=\color{commentgrey},
+  frame=single, rulecolor=\color{backgray}, showstringspaces=false,
+  breakatwhitespace=true, breaklines=true, upquote=true,
+  numbers=left, numberstyle=\footnotesize\color{commentgrey}}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% User-defined LaTeX commands
+\DeclareMathOperator{\Var}{Var}
+\DeclareMathOperator{\Cov}{Cov}
+\DeclareMathOperator{\Corr}{Corr}
+\DeclareMathOperator*{\argmax}{arg\,max}
+\DeclareMathOperator*{\argmin}{arg\,min}
+\DeclarePairedDelimiter{\abs}{\lvert}{\rvert}
+\DeclarePairedDelimiter{\norm}{\lVert}{\rVert}
+\newcommand*{\expp}[1]{\exp\left(#1\right)}
+\newcommand*{\foralls}{\ \forall \ }
+\newcommand*{\st}{\text{ s.t. }}
+\newcommand*{\E}{\mathbb E}
+\newcommand*{\R}{\mathbb R}
+\newcommand*{\I}{\mathds{1}}
+\newcommand*{\Prob}{\mathbb P}
+\newcommand*{\convas}[1]{\xrightarrow{#1}}
+\newcommand*{\conv}{\convas{}}
+\newcommand*{\cond}{\;\ifnum\currentgrouptype=16 \middle\fi|\;}
+\newcommand*{\defeq}{%
+  \mathrel{\overset{\makebox[0pt]{\mbox{\normalfont\tiny\sffamily def}}}{=}}}
+\newcommand*{\notorth}{\ensuremath{\perp\!\!\!\!\!\!\diagup\!\!\!\!\!\!\perp}}
+\newcommand*{\orth}{\ensuremath{\perp\!\!\!\perp}}
+\newcommand*{\evalat}{\,\big\rvert}
+\newcommand*{\dif}{\,d}
+\newcommand*{\difto}[1]{\,d^#1}
+\newcommand*{\difbot}[1]{\frac{d}{d#1}}
+\newcommand*{\partialbot}[1]{\frac{\partial}{\partial#1}}
+\newcommand*{\m}[1]{\textbf{#1}}
+\newcommand*{\bmath}[1]{\boldsymbol{#1}}
+
+\newcommand*{\yestag}{\addtocounter{equation}{1}\tag{\theequation}}
+\newcommand*{\notaligned}[1]{\noalign{$\displaystyle #1$}}
+\newcommand*{\ttilde}{{\raise.17ex\hbox{$\scriptstyle\sim$}}}
+
+\makeatletter
+\newsavebox{\mybox}\newsavebox{\mysim}
+\newcommand*{\distas}[1]{%
+  \savebox{\mybox}{\hbox{\kern3pt$\scriptstyle#1$\kern3pt}}%
+  \savebox{\mysim}{\hbox{$\sim$}}%
+  \mathbin{\overset{#1}{\kern\z@\resizebox{\wd\mybox}{\ht\mysim}{$\sim$}}}%
+}
+\makeatother
+\newcommand*{\dist}{\sim}
+\newcommand*{\distiid}{\distas{\text{i.i.d}}}
+
+\makeatletter
+\def\moverlay{\mathpalette\mov@rlay}
+\def\mov@rlay#1#2{\leavevmode\vtop{%
+   \baselineskip\z@skip \lineskiplimit-\maxdimen
+   \ialign{\hfil$\m@th#1##$\hfil\cr#2\crcr}}}
+\newcommand*{\charfusion}[3][\mathord]{
+  #1{\ifx#1\mathop\vphantom{#2}\fi\mathpalette\mov@rlay{#2\cr#3}}
+  \ifx#1\mathop\expandafter\displaylimits\fi}
+\makeatother
+\newcommand*{\cupdot}{\charfusion[\mathbin]{\cup}{\cdot}}
+\newcommand*{\bigcupdot}{\charfusion[\mathop]{\bigcup}{\cdot}}
+
+\newcommand*{\mt}[1]{\text{\normalfont #1}}
+
+\newtheorem{theorem}{Theorem}[section]
+\newtheorem{theorem*}{Theorem}
+\newtheorem{corollary}{Corollary}[section]
+\newtheorem{proposition}{Proposition}[section]
+\newtheorem{lemma}{Lemma}[section]
+
+\theoremstyle{definition}
+\newtheorem{definition}{Definition}[section]
+\newtheorem{definition*}{Definition}
+\newtheorem{example}{Example}[section]
+\newtheorem*{properties}{Properties}
+
+\newtheoremstyle{algodesc}{}{}{}{}{\bfseries}{.}{ }{}%
+\theoremstyle{algodesc}
+\newtheorem{algodesc}{Algorithm}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
+\title{Exploring Hillary Clinton's Emails\thanks{STATS 601 final project.}}
+\author{
+    Leland Bybee, Roger Fan, Ryan Vaughn
+}
+\date{\today}
+
+\maketitle
+
 \section{Introduction}
 
-\section{Data Summary}
+\section{Data}
 
-\section{MDS}
+\section{Visualization}
+Motivation, cosine distance
 
-\section{Spectral Clustering}
+\subsection{Multidimensional Scaling}
 
-\section{TM Background/Estimation}
+\subsection{Spectral Clustering}
 
-\section{Interpreting Topics/Model Selection}
+\section{Topic Modeling}
+Include model description, estimation strategy, and model selection.
 
-\section{Types of Topics}
+\subsection{Interpreting Topics}
+Include ``grunt work'' of interpreting topics, topic frequency
 
-\section{Interesting Topics}
+\subsection{Types of Topics}
+Talk about structural, common word, and semantic topics, including ``interesting'' vs. ``non-interesting'' topics, discuss strengths of model in comparison to MDS
 
-\section{Who Says What/Multinomial Regression}
+\subsection{Topic Analysis}
+Analyze some specific topics, compare use over time and how it correlates with related events
+
+\section{Email Sender Prediction}
+Talk about the who says what table
+
+\subsection{Multinomial Logistic Regression}
+Quickly describe model and discuss results
 

### 2016-04-18 code/mds.py
Adjusting mds images.

@@ -86,7 +86,7 @@ fig = plt.figure()
 ax = fig.add_subplot(111)
 ax.scatter(z1, z2, s=10, lw=0.15)
 fig.savefig('../images/mds_2d.pdf', bbox_inches='tight')
-fig.savefig('../images/mds_2d.png', bbox_inches='tight', dpi=900)
+fig.savefig('../images/mds_2d.png', bbox_inches='tight', dpi=400)
 
 fig = plt.figure()
 ax = fig.add_subplot(111)
@@ -95,7 +95,7 @@ for g, c in zip(range(10), colors):
                c=c, s=10, lw=0.15, label=str(g))
 ax.legend(scatterpoints=1, markerscale=2)
 fig.savefig('../images/mds_2d_cluster.pdf', bbox_inches='tight')
-fig.savefig('../images/mds_2d_cluster.png', bbox_inches='tight', dpi=900)
+fig.savefig('../images/mds_2d_cluster.png', bbox_inches='tight', dpi=400)
 
 
 fig = plt.figure()
@@ -103,11 +103,11 @@ ax = fig.add_subplot(111, projection='3d')
 ax.scatter(z1, z2, z3, s=10, lw=0.15)
 ax.view_init(29, 46)
 fig.savefig('../images/mds_3d_1.pdf', bbox_inches='tight')
-fig.savefig('../images/mds_3d_1.png', bbox_inches='tight', dpi=900)
+fig.savefig('../images/mds_3d_1.png', bbox_inches='tight', dpi=400)
 
 ax.view_init(-10, 227)
 fig.savefig('../images/mds_3d_2.pdf', bbox_inches='tight')
-fig.savefig('../images/mds_3d_2.png', bbox_inches='tight', dpi=900)
+fig.savefig('../images/mds_3d_2.png', bbox_inches='tight', dpi=400)
 
 fig = plt.figure()
 ax = fig.add_subplot(111, projection='3d')
@@ -117,11 +117,11 @@ for g, c in zip(range(10), colors):
 ax.legend(scatterpoints=1, markerscale=2)
 ax.view_init(29, 46)
 fig.savefig('../images/mds_3d_cluster_1.pdf', bbox_inches='tight')
-fig.savefig('../images/mds_3d_cluster_1.png', bbox_inches='tight', dpi=900)
+fig.savefig('../images/mds_3d_cluster_1.png', bbox_inches='tight', dpi=400)
 
 ax.view_init(-10, 227)
[…]

### 2016-04-18 paper/paper.tex
Working on figures/tables.

@@
 \usepackage{graphicx}
-\usepackage{color}
+\usepackage{xcolor}
 \usepackage{titlesec}
@@
 \usepackage{dsfont}
+
+\usepackage{tikz}
 
@@
 
+\newcommand*{\colsquare}[3][-3.5pt]{\tikz[baseline=-0.5ex]\draw[#2, fill=#2] (0,#1) rectangle ++(#3,#3);}%
+\definecolor{cmeet}{HTML}{E31A1C}
+\definecolor{cmideast}{HTML}{1F78B4}
+\definecolor{cstaff}{HTML}{A6CEE3}
+\definecolor{cpolitics}{HTML}{33A02C}
+\definecolor{cterror}{HTML}{B2DF8A}
+\definecolor{cforeign}{HTML}{FB9A99}
+\definecolor{cpress}{HTML}{FF7F00}
+\definecolor{chill}{HTML}{6A3D9A}
+\definecolor{ccommu}{HTML}{CAB2D6}
+\definecolor{ccomm}{HTML}{FDBF6F}
+
 \begin{document}
@@
 
+We define the cosine similarity between word frequency vectors $V$ and $W$ to be the cosine of the angle between the two vectors, calculated as
+\begin{equation} \label{eq:cos_sim}
+\cos(\phi) = \frac{\langle V, W \rangle}{\norm{V}\norm{W}}
+\end{equation}
+Since counts must be nonnegative, note that $\phi \leq \pi/2$.
+This implies that the cosine similarity is always between 0 and 1, with 0 corresponding to parallel vectors and 1 corresponding to orthogonal vectors.
+So we can define the cosine distance as
+\begin{equation} \label{eq:cos_dist}
+d(V, W) = 1 - \cos(\phi) = 1 - \frac{\langle V, W \rangle}{\norm{V}\norm{W}}
+\end{equation}
+
+\begin{figure}[htb] \centering
+  \begin{subfigure}[t]{.49\linewidth}
+    \includegraphics[width=\linewidth]{../images/mds_2d.png}
+    \caption{2 Dimensions} \label{fig:mds:2d}
+  \end{subfigure}
+  \begin{subfigure}[t]{.49\linewidth}
+    \includegraphics[width=\linewidth]{../images/mds_3d_1.png}
+    \caption{3 Dimensions} \label{fig:mds:3d}
+  \end{subfigure}
+  \caption{Visualization of a 8,000 email subset using classical multi-dimensional scaling. The distance metric used is cosine distance as defined in Equation~\ref{eq:cos_dist}.}
+  \label{fig:mds}
+\end{figure}
+
+\begin{figure}[htbp] \centering
+  \begin{subfigure}[t]{.7\linewidth}
+    \includegraphics[width=\linewidth]{../images/mds_2d_cluster.png}
+    \caption{2 Dimensions} \label{fig:cluster:2d}
+  \end{subfigure}
+  \begin{subfigure}[t]{.7\linewidth}
+    \includegraphics[width=\linewidth]{../images/mds_3d_cluster_1.png}
+    \caption{3 Dimensions} \label{fig:cluster:3d}
+  \end{subfigure}
+  \caption{Visualization of the same 8,000 email subset with coloring according to the results from spectral clustering.}
+  \label{fig:cluster}
+\end{figure}
+
 \subsection{Multidimensional Scaling}
@@
 Include ``grunt work'' of interpreting topics, topic frequency
+
+\begin{table}[htb] \centering
+\begin{tabular}{rcl}
+  \toprule
+  \colsquare{cterror}{10pt} & Terrorism & 5, 22 \\
+  \colsquare{cmideast}{10pt} & Middle East & 6, 18, 19, 27, 29 \\
+  \colsquare{cforeign}{10pt} & Foreign Policy & 2, 7, 13, 21, 23, 26 \\
+  \colsquare{cpolitics}{10pt} & Politics & 11, 17, 25 \\
+  \colsquare{cstaff}{10pt} & Staff & 16, 20 \\
+  \colsquare{cpress}{10pt} & Press & 4 \\
+  \colsquare{chill}{10pt} & Hillary & 12 \\
+  \colsquare{cmeet}{10pt} & Meetings & 9, 10, 24, 28, 30 \\
+  \colsquare{ccommu}{10pt} & Communication & 1 \\
+  \colsquare{ccomm}{10pt} & Common & 3, 8, 14, 15 \\
+  \bottomrule
+\end{tabular}
+\caption{Topic Categorization}
+\label{tab:topic_cat}
+\end{table}
+
+\begin{table}[htb] \centering
+\setlength{\tabcolsep}{1pt}
+\begin{tabular}{ccccccccccccccccccccccccc}
+  \toprule
+  \colsquare[-3pt]{cforeign}{16pt} &
+  \colsquare[-3pt]{cmeet}{16pt} &
+  \colsquare[-3pt]{cmeet}{16pt} &
+  \colsquare[-3pt]{cmeet}{16pt} &
+  \colsquare[-3pt]{cmeet}{16pt} &
+  \colsquare[-3pt]{cpress}{16pt} &
+  \colsquare[-3pt]{cmeet}{16pt} &
+  \colsquare[-3pt]{cmideast}{16pt} &
+  \colsquare[-3pt]{cmideast}{16pt} &
+  \colsquare[-3pt]{cstaff}{16pt} &
+  \colsquare[-3pt]{cstaff}{16pt} &
+  \colsquare[-3pt]{chill}{16pt} &
+  \colsquare[-3pt]{cforeign}{16pt} &
+  \colsquare[-3pt]{cpolitics}{16pt} &
+  \colsquare[-3pt]{cmideast}{16pt} &
+  \colsquare[-3pt]{cmideast}{16pt} &
+  \colsquare[-3pt]{cforeign}{16pt} &
+  \colsquare[-3pt]{cmideast}{16pt} &
+  \colsquare[-3pt]{cterror}{16pt} &
+  \colsquare[-3pt]{cforeign}{16pt} &
+  \colsquare[-3pt]{cpolitics}{16pt} &
+  \colsquare[-3pt]{cforeign}{16pt} &
+  \colsquare[-3pt]{cforeign}{16pt} &
+  \colsquare[-3pt]{cpolitics}{16pt} &
+  \colsquare[-3pt]{cterror}{16pt} \\
+  21 & 28 & 30 & 9 & 10 & 4 & 24 & 29 & 18 & 20 & 16 & 12 &
+  13 & 17 & 19 & 27 & 23 & 6 & 22 & 2 & 25 & 26 & 7 & 11 & 5 \\
+  \bottomrule
+\end{tabular}
+\setlength{\tabcolsep}{6pt}
+\caption{Primary Topic Frequency}
+\label{tab:topic_freq}
+\end{table}
 

### 2016-04-18 code/topic_regression.R
Adding legend, cleaning up graphing.

@@ -25,7 +25,7 @@ data <- data[data$Person %in% people,]
 rows <- length(data[,1])
 
 test_ind <- sample(1:rows, rows/10)
-train_ind <- 1:rows[!(1:rows %in% test_ind)]
+train_ind <- (1:rows)[!(1:rows %in% test_ind)]
 
 training <- data[train_ind,]
 testing <- data[test_ind,]
@@ -57,17 +57,41 @@ coefficients <- scale(coefficients)
 #    coefficients[,i] <- (coefficients[,i] - min(coefficients[,i])) / (max(coefficients[,i]) - min(coefficients[,i]) + 0.0000001)
 #}
 #coefficients <- coefficients - mean(as.matrix(coefficients))
-test <- c("Meetings", "Middle East", "Staff", "Politics", "Terrorism", "Foreign Policy", "Press", "Hillary", "Communication", "Common")
-col <- c('#e31a1c','#1f78b4','#a6cee3','#33a02c','#b2df8a','#fb9a99','#ff7f00','#6a3d9a','#cab2d6','#fdbf6f')
-sortorder <- c(5, 22, 6, 18, 19, 27, 29, 2, 7, 13, 21, 23, 26, 11, 17, 25, 16, 20, 4, 12, 9, 10, 24, 28, 30, 1, 3, 8, 14, 15)
-colororder <- c(rep(col[5], 2), rep(col[2], 5), rep(col[6], 6), rep(col[4], 3), rep(col[3], 2), rep(col[7], 1), rep(col[8], 1), rep(col[1], 5), rep(col[9], 1), rep(col[10], 4))
+test <- c("Meetings", "Middle East", "Staff",   "Politics", "Terrorism", "Foreign Policy", "Press",   "Hillary", "Common")
+col <-  c('#b2df8a',  '#fdbf6f',     '#a6cee3', '#33a02c',  '#e31a1c',   '#ff7f00',        '#fb9a99', '#6a3d9a', '#1f78b4')
+sortorder <- c(5, 22, 6, 18, 19, 27, 29, 2, 7, 13, 21, 23, 26, 11, 17, 25, 16, 20, 4, 12, 1, 9, 10, 24, 28, 30, 3, 8, 14, 15)
+colororder <- c(rep(col[5], 2), rep(col[2], 5), rep(col[6], 6), rep(col[4], 3), rep(col[3], 2), rep(col[7], 1), rep(col[8], 1), rep(col[1], 6), rep(col[9], 4))
[…]

### 2016-04-18 code/topic_regression.R
Updated image.

@@ -91,7 +91,7 @@ gplot = ggplot(data=mlt, aes(x=Topic, y=Sender)) +
     theme(legend.key=element_blank(), panel.background=element_rect(fill="white", colour="white"),
           axis.text.x=element_text(color=colororder, angle=90, hjust=0, vjust=0.5))
 
-pdf('./coefficients.pdf', height=5.5, width=7, family='CM Roman')
+pdf('../images/coefficients.pdf', height=5.5, width=7, family='CM Roman')
 print(gplot)
 dev.off()
 

### 2016-04-18 code/topic_regression.R
Minor adjustments.

@@ -52,7 +52,7 @@ coefficients <- data.frame(coef(fit))
 coefficients <- coefficients[,2:(K+1)]
 #coefficients[coefficients < -1] <- -1
 #coefficients[coefficients < 0] <- 0
-coefficients <- scale(coefficients)
+coefficients <- scale(coefficients, center=FALSE)
 #for(i in 1:K){
 #    coefficients[,i] <- (coefficients[,i] - min(coefficients[,i])) / (max(coefficients[,i]) - min(coefficients[,i]) + 0.0000001)
 #}
@@ -79,19 +79,18 @@ legend = c('Terrorism'='#e31a1c',
            'Hillary'='#6a3d9a',
            'Meetings'='#b2df8a',
            'Common'='#1f78b4')
-
 a = data.frame(x=rep(1, 9), y=rep(1, 9), z=cats)
 
 gplot = ggplot(data=mlt, aes(x=Topic, y=Sender)) +
     geom_tile(aes(fill=Coefficient), color="white") +
-    geom_line(data=a, aes(x=x, y=y, color=z), alpha=0.0) +
+    geom_line(data=a, aes(x=x, y=y, color=z), alpha=0.0, size=1.3) +
     scale_fill_gradient2(midpoint=0, low="#4d9221", high="#c51b7d") +
     scale_color_manual(name='Category', values=legend, breaks=cats) +
     guides(color=guide_legend(override.aes=list(alpha=1))) +
     theme(legend.key=element_blank(), panel.background=element_rect(fill="white", colour="white"),
           axis.text.x=element_text(color=colororder, angle=90, hjust=0, vjust=0.5))
 
-pdf('../images/coefficients.pdf', height=5.5, width=7, family='CM Roman')
+pdf('../images/coefficients.pdf', height=5.5, width=6.5, family='CM Roman')
 print(gplot)
 dev.off()
 

### 2016-04-18 paper/paper.tex
Adjusting colors.
Minor adjustments.
Minor changes.

@@
 \newcommand*{\colsquare}[3][-3.5pt]{\tikz[baseline=-0.5ex]\draw[#2, fill=#2] (0,#1) rectangle ++(#3,#3);}%
-\definecolor{cmeet}{HTML}{E31A1C}
-\definecolor{cmideast}{HTML}{1F78B4}
+\definecolor{cmeet}{HTML}{B2DF8A}
+\definecolor{cmideast}{HTML}{FDBF6F}
 \definecolor{cstaff}{HTML}{A6CEE3}
 \definecolor{cpolitics}{HTML}{33A02C}
-\definecolor{cterror}{HTML}{B2DF8A}
-\definecolor{cforeign}{HTML}{FB9A99}
-\definecolor{cpress}{HTML}{FF7F00}
+\definecolor{cterror}{HTML}{E31A1C}
+\definecolor{cforeign}{HTML}{FF7F00}
+\definecolor{cpress}{HTML}{FB9A99}
 \definecolor{chill}{HTML}{6A3D9A}
-\definecolor{ccommu}{HTML}{CAB2D6}
-\definecolor{ccomm}{HTML}{FDBF6F}
+\definecolor{ccomm}{HTML}{1F78B4}
 
@@
 
-\begin{figure}[htb] \centering
-  \begin{subfigure}[t]{.49\linewidth}
-    \includegraphics[width=\linewidth]{../images/mds_2d.png}
-    \caption{2 Dimensions} \label{fig:mds:2d}
-  \end{subfigure}
-  \begin{subfigure}[t]{.49\linewidth}
-    \includegraphics[width=\linewidth]{../images/mds_3d_1.png}
-    \caption{3 Dimensions} \label{fig:mds:3d}
-  \end{subfigure}
-  \caption{Visualization of a 8,000 email subset using classical multi-dimensional scaling. The distance metric used is cosine distance as defined in Equation~\ref{eq:cos_dist}.}
-  \label{fig:mds}
-\end{figure}
-
 \begin{figure}[htbp] \centering
@@
   \end{subfigure}
-  \caption{Visualization of the same 8,000 email subset with coloring according to the results from spectral clustering.}
+  \caption{Visualization of a 8,000 email subset using classical multi-dimensional scaling and with coloring according to the results from spectral clustering.
+The similarity and distance metrics used for spectral clustering and MDS, respectively, are cosine similarity and distance as defined in Equations~\ref{eq:cos_sim} and~\ref{eq:cos_dist}.}
   \label{fig:cluster}
@@
   \colsquare{chill}{10pt} & Hillary & 12 \\
-  \colsquare{cmeet}{10pt} & Meetings & 9, 10, 24, 28, 30 \\
-  \colsquare{ccommu}{10pt} & Communication & 1 \\
+  \colsquare{cmeet}{10pt} & Meetings & 1, 9, 10, 24, 28, 30 \\
   \colsquare{ccomm}{10pt} & Common & 3, 8, 14, 15 \\
@@
 \setlength{\tabcolsep}{1pt}
-\begin{tabular}{ccccccccccccccccccccccccc}
+\begin{tabular}{cccccccccccccccccccccccccc}
   \toprule
   \colsquare[-3pt]{cforeign}{16pt} &
+  \colsquare[-3pt]{cmeet}{16pt} &
   \colsquare[-3pt]{cmeet}{16pt} &
@@
   \colsquare[-3pt]{cstaff}{16pt} &
+  \colsquare[-3pt]{chill}{16pt} &
   \colsquare[-3pt]{cstaff}{16pt} &
-  \colsquare[-3pt]{chill}{16pt} &
+  \colsquare[-3pt]{cpolitics}{16pt} &
   \colsquare[-3pt]{cforeign}{16pt} &
-  \colsquare[-3pt]{cpolitics}{16pt} &
-  \colsquare[-3pt]{cmideast}{16pt} &
   \colsquare[-3pt]{cmideast}{16pt} &
@@
   \colsquare[-3pt]{cterror}{16pt} &
+  \colsquare[-3pt]{cmideast}{16pt} &
   \colsquare[-3pt]{cforeign}{16pt} &
@@
   \colsquare[-3pt]{cterror}{16pt} \\
-  21 & 28 & 30 & 9 & 10 & 4 & 24 & 29 & 18 & 20 & 16 & 12 &
-  13 & 17 & 19 & 27 & 23 & 6 & 22 & 2 & 25 & 26 & 7 & 11 & 5 \\
+  21 & 1 & 28 & 30 & 10 & 9 & 4 & 24 & 18 & 29 & 16 & 12 & 20 &
+  17 & 13 & 19 & 23 & 27 & 22 & 6 & 2 & 25 & 26 & 7 & 11 & 5 \\
+  \midrule
+  \multicolumn{13}{l}{Most Frequent} & \multicolumn{13}{r}{Least Frequent} \\
   \bottomrule
@@
 
+\begin{figure}[htb] \centering
+  \includegraphics[width=0.95\linewidth]{../images/coefficients.pdf}
+  \caption{Normalized coefficients from a multinomial logistic regression of email sender on LDA topic proportions.}
+  \label{fig:coefficients}
+\end{figure}
+
 \section{Conclusion}

### 2016-04-18 code/topic_regression.R
Updating image.

@@ -52,7 +52,7 @@ coefficients <- data.frame(coef(fit))
 coefficients <- coefficients[,2:(K+1)]
 #coefficients[coefficients < -1] <- -1
 #coefficients[coefficients < 0] <- 0
-coefficients <- scale(coefficients, center=FALSE)
+coefficients <- scale(coefficients)
 #for(i in 1:K){
 #    coefficients[,i] <- (coefficients[,i] - min(coefficients[,i])) / (max(coefficients[,i]) - min(coefficients[,i]) + 0.0000001)
 #}

### 2016-04-18 paper/paper.tex
Writing writing writing.

@@
 \usepackage{float}
+\usepackage{tabularx}
+\usepackage{ragged2e}
+\newcolumntype{Y}{>{\RaggedRight\arraybackslash}X}
+\usepackage{pdflscape}
+\usepackage{afterpage}
 
@@
 \section{Introduction}
+From roughly 2008 to 2013, Hillary Clinton and some of her staff used a private family email server for most of he communication.
+This time period includes her tenure as U.S.
+Secretary of State, and has therefore become a controversial topic due to the possible security concerns of not using official government servers.
+Various investigations into the legality and appropriateness of the email server have been launched, and the issue has had/will potentiall have a large effect on Clinton's ongoing presidential campaign.
+
+Due to several Freedom of Information Act (FOIA), the State Department has released the vast majority of the roughly 55,000 pages of emails to the public, leading to an unprecedented opportunity to explore the email usage of a major public figure.
+
+Due to the size of the corpus, reading individual emails in the hope of discovering interesting characteristics is unrealistic.
+We therefore exploit statistical methods to break this vast analysis problem to a more manageable one, decreasing the scale so that we can more easily apply human and statistical analysis.
+
+In order to tackle this problem, we use classical multi-dimensional scaling and spectral clustering in order to visualize and explore the corpus.
+We also use a statistical topic model, latent Dirichlet analysis (LDA), in order to identify and analyze the meanings and semantics.
+Finally, we use the LDA results and other metadata to examine how other covariates, such as email sender and time period sent, are related to the topic of an email.
 
 \section{Data}
+The State Department released the raw data in the form of roughly 30,000 pdfs of individual emails from the Clinton server.\footnote{Thanks to Ben Hamner and the Wall Street Journal for making the data processing code (\url{https://github.com/benhamner/hillary-clinton-emails}) and email pdfs (\url{http://graphics.wsj.com/hillary-clinton-email-documents/}) available, respectively.} We first process the pdfs to extract the raw text.\footnote{We used \texttt{pdftotext}, an open-source program used to extract text from pdf files.} From the raw email text, email headers and forward/response information are stripped, leaving only the subject line and body text.
+
+All of our methods use a bag-of-words model, so from this raw data we construct a document term matrix containing vectors of word counts.
+Some standard data cleaning for text data is also performed, including the removal of punctuation and email addresses, word stemming (combining words with common roots, e.g.
+calling and called), and removing extremely common words (i.e.
+stop words) and extremely rare words (words that appear in less than 0.1\% of emails).
+
+After this processing, we are left with a dataset of roughly 28,000 emails and a total vocabulary of over 3,000 words.
+Note that each word count vector is extremely sparse, so we need statistical methods that can apply in a sparse coordinate setting.
+Also, methods that can efficiently exploit this sparseness to reduce computation are preferred.
 
 \section{Visualization}
-Motivation, cosine distance
+Due to the large size and high dimensionality of the data, we must apply some dimensionality reduction in order to effectively visualize it.
+We therefore apply classical multi-dimensional scaling, which attempts to place each point in a much smaller dimension such that pairwise distances are preserved.
+
+However, we expect standard Euclidean distance to poorly capture the actual relationships between vectors of word counts.
+In particular, Euclidean distance is affected by the total number of words, two emails with the exact same word distribution that differ in length could have a very large distance between them.
+In order to better capture pairwise relationships, we will use a distance metric based on the angles between vectors.
 
@@
 Since counts must be nonnegative, note that $\phi \leq \pi/2$.
-This implies that the cosine similarity is always between 0 and 1, with 0 corresponding to parallel vectors and 1 corresponding to orthogonal vectors.
+This implies that the cosine similarity is always between 0 and 1, with 0 corresponding to vectors that are multiples of each other and 1 corresponding to orthogonal vectors (i.e.
+no shared words).
 So we can define the cosine distance as
@@
 \end{equation}
+
+Using this measure of distance, we can construct a distance matrix $D$ and apply MDS.
+The results for an 8,000 email subset are shown in Figure~\ref{fig:cluster}, plotted in both two and three dimensions.
+We can see several interesting patterns.
+The vast majority of emails (roughly 5,000) are contained in the main central grouping, with two large groupings that extend away.
+Besides these two ``arms,'' however, it is difficult to visually identify other significant structures.
 
@@
 
-\subsection{Multidimensional Scaling}
+\subsection{Spectral Clustering}
+In order to better identify structure that may exist in the data, we attempt to apply clustering methods.
+However, it is important to choose an appropriate clustering method due to the high dimensionality and sparse nature of the data.
+In particular, we expect centroid-based methods such as Gaussian mixture models and $k$-means clustering to perform poorly in this setting.
 
-\subsection{Spectral Clustering}
+Spectral clustering, however, exploits the information contained in the pairwise distances (or, equivalently, the similarities) between points.
+By using pairwise distances, spectral clustering is particularly well-suited to finding clusters that may not necessarily be spherical or ellipsoidal and that may lie along lower-dimensional manifolds.
+
+To actually apply spectral clustering, we first construct the pairwise similarity matrix $S$ using our cosine similarity as defined in Equation~\ref{eq:cos_sim}.
+We define the degree matrix $D$ to be a diagonal matrix with $D_{ii} = \sum_j S_{ij}$, and construct the symmatrix normalized Laplacian matrix as
+\begin{equation} \label{eq:laplacian}
+L = I - D^{-1/2} S D^{-1/2}
+\end{equation}
+Then the eigenvectors corresponding to the smallest $k$ eigenvalues of $L$ are computed and $k$-means clustering is performed on these eigenvectors.
+
+Figure~\ref{fig:cluster} classifies each point according to the results of spectral clustering with $k$ clusters.
+We can see that many of the cluster correspond to  the visually identifiable structures, including clusters that correspond to each of the ``arms.''
+
+By investigating the individual emails, we can also get a sense of what each cluster consists of.
+For instance, clusters 2 and 4 consist of emails related to calls and communication.
+In this arm, those closer to the main central clump contain more conversation, while those farther out are much briefer and directly about the call (e.g.
+``I'd like to call tomorrow.'').
+Cluster 3 consists entirely of ``minis,'' summaries of the days schedule sent to Clinton each morning.
+Emails from cluster 5 are generally requests to print materials, while those from cluster 6 are forwarded news articles.
+
+In general, it seems that spectral clustering does a good job at identifying emails by their structure, but does not tell us much about the meaning of an email.
+We can tell that an email is regarding a call or is a news headline by what cluster it is in, but not what that call or headline is about.
+On a related note, it does not do a good job separating the ``regular'' emails.
+OVer 5,000 of the 8,000 emails depicted fall into clusters 1 or 8, which essentially consist of all the emails without specific identifiable structure.
+Ideally we would be able to further classify these emails according to subject matter, but clustering does not seem suited to this task.
 

### 2016-04-19 paper/paper.tex
add figures to paper

@@
 
+\begin{table}[h]
+\centering
+\label{topic_top_words}
+\scalebox{0.8}{
+\begin{tabular}{cccccc}
+\toprule
+Israel & Elections & Libya & Afghanistan & Int. Dev. & Obama \\
+\midrule
+israel & democrat & libya & afghanistan & develop & presid \\
+isra & republican & secur & pakistan & state & obama \\
+peace & american & travel & afghan & support & said \\
+palestinian & polit & libyan & militari & global & hous \\
+netanyahu & parti & iraq & general & program & white \\
+east & elect & embassi & karzai & effort & administr \\
+negoti & obama & attack & offici & intern & polici \\
+arab & percent & kill & war & work & aid \\
+state & candid & march & forc & includ & advis \\
+\bottomrule
+\end{tabular}
+}
+\caption{Some interesting content topics}
+\label{tab:content_topics}
+\end{table}
+
+\begin{figure}[h]
+\centering
+\begin{subfigure}[Israel]{.30\linewidth}
+    \includegraphics[width=\linewidth]{../images/time_plot6.pdf}
+    \caption{Israel} \label{fig:t1}
+\end{subfigure}
+\begin{subfigure}[Election]{.30\linewidth}
+    \includegraphics[width=\linewidth]{../images/time_plot11.pdf}
+    \caption{Election} \label{fig:t2}
+\end{subfigure}
+\begin{subfigure}[Libya]{.30\linewidth}
+    \includegraphics[width=\linewidth]{../images/time_plot18.pdf}
+    \caption{Libya} \label{fig:t3}
+\end{subfigure}
+\begin{subfigure}[Afghanistan]{.30\linewidth}
+    \includegraphics[width=\linewidth]{../images/time_plot27.pdf}
+    \caption{Afghanistan} \label{fig:t4}
+\end{subfigure}
+\begin{subfigure}[Int. Dev.]{.30\linewidth}
+    \includegraphics[width=\linewidth]{../images/time_plot23.pdf}
+    \caption{Int. Dev.} \label{fig:t5}
+\end{subfigure}
+\begin{subfigure}[Obama]{.30\linewidth}
+    \includegraphics[width=\linewidth]{../images/time_plot25.pdf}
+    \caption{Obama} \label{fig:t6}
+\end{subfigure}
+\label{fig:topic_time_plots}
+\end{figure}
+
 \section{Email Sender Prediction}
 Talk about the who says what table
+
+\begin{table}[h]
+\centering
+\label{topic_sources}
+\scalebox{0.70}{
+\begin{tabular}{cccccc}
+\toprule
+Israel & Elections & Libya & Afghanistan & Int. Dev. & Obama \\
+\midrule
+Sidney Blumenthal & SB & Huma Abedin & Judith McHale & JM & SB \\
+(SB) & & (HA) & (JM) & & \\
+\noalign{\vskip 5mm}
+HA & Philippe Reines & Wendy Sherman & HA & Melanne Verveer & PR \\
+& (PR) & (WS) & & (MV) & \\
+\noalign{\vskip 5mm}
+Jake Sullivan & JM & JS & MV & Anne-Marie & Cherly Mills \\
+(JS) & & & & Slaughter (AMS) & (CM)\\
+\noalign{\vskip 5mm}
+AMS & CM & Monica Hanley & JS & CM & HA \\
+& & (MH) & & & \\
+\noalign{\vskip 5mm}
+Hillary Clinton & HA & SB & Richard Verma & JS & HC \\
+(HC) & & & (RV) & & \\
+\bottomrule
+\end{tabular}
+}
+\caption{Primary sources for interesting topics}
+\label{tab:top_sources}
+\end{table}
 
@@
   \includegraphics[width=0.95\linewidth]{../images/coefficients.pdf}
-  \caption{Normalized coefficients from a multinomial logistic regression of email sender on LDA topic proportions.}
+  \caption{Standardized coefficients from a multinomial logistic regression of email sender on LDA topic proportions.}
   \label{fig:coefficients}

### 2016-04-19 code/topic_month_plots.R

@@ -1,6 +1,7 @@
 library(lubridate)
 library(ggplot2)
 library(tm)
+library(extrafont)
 
 K <- 30
 
@@ -17,7 +18,9 @@ temp <- agg[,2:(K+1)]
 agg <- aggregate(temp, list(agg$Date), mean)
 
 for(i in seq(2, K+1, 1)){
-    ggplot() + geom_line(aes(x=agg[,1], y=agg[,i])) + xlab("Date") + ylab("Topic Proportion")
-    ggsave(paste("time_plot", i-1, ".pdf", sep=""))
+    gplot <- ggplot() + geom_line(aes(x=agg[,1], y=agg[,i])) + xlab("Date") + ylab("Topic Proportion")
+    pdf(paste('../images/time_plot', i-1, '.pdf', sep=""), height=5.5, width=6.5, family='CM Roman')
+    print(gplot)
+    dev.off()
 }
 

### 2016-04-19 code/topic_time_plots.R

@@ -1,5 +1,6 @@
 library(ggplot2)
 library(tm)
+library(extrafont)
 
 K <- 30
 
@@ -12,6 +13,8 @@ agg <- agg[agg$Group.1 >= as.Date("2009-03-18"),]
 agg <- agg[agg$Group.1 < as.Date("2013-02-01"),]
 
 for(i in seq(2, K+1, 1)){
-    ggplot() + geom_line(aes(x=agg[,1], y=agg[,i])) + xlab("Date") + ylab("Topic Proportion")
-    ggsave(paste("time_plot", i-1, ".pdf", sep=""))
+    gplot <- ggplot() + geom_line(aes(x=agg[,1], y=agg[,i])) + xlab("Date") + ylab("Topic Proportion")
+    pdf(paste('../images/time_plot', i-1, '.pdf', sep=""), height=5.5, width=6.5, family='CM Roman')
+    print(gplot)
+    dev.off()
 }

### 2016-04-19 paper/paper.tex
add my section of the paper and a very rough copy of Ryan's

@@
 In order to tackle this problem, we use classical multi-dimensional scaling and spectral clustering in order to visualize and explore the corpus.
-We also use a statistical topic model, latent Dirichlet analysis (LDA), in order to identify and analyze the meanings and semantics.
+We also use a statistical topic model, latent Dirichlet allocation (LDA), in order to identify and analyze the meanings and semantics.
 Finally, we use the LDA results and other metadata to examine how other covariates, such as email sender and time period sent, are related to the topic of an email.
@@
 \section{Topic Modeling}
-Include model description, estimation strategy, and model selection.
+
+To try and move beyond the limitations of spectral clustering and capture some of the content of the emails as well as structure, we next turn to latent Dirichlet allocation (LDA).
+LDA is a popular form of topic modeling that has historically been effective for identifying clusters or "topics" in text corpuses\footnote{note on estimation}.
+
+LDA requires the number of topics to be specified as an input to the model, therefore one of the preliminary steps for topic model estimation is the selection of an appropriate number of topics.
+Since our ultimate goal was to find sensible topics that could be used to understand the email corpus we initially turned to several coherence measures to perform our model selection, in particular we considered the UMass and UCI measures\footnote{add bib here}.
+Coherence measures were developed as a way to quantify whether topics could make sense to a human observer.
+However, the coherence of our topics didn't appear to vary much assuming we used more than 15 topics and less than 50.
+As a result we turned to manual methods for selecting the number of topics that appeared to perform the best.
+We estimated LDA for 5,10,...,75 topics and selected the model that appeared to be the most sensible to a human observer.
+This left us with a 30 topic model.
+
+Using our resulting topic model we want to answer a series of questions concerning our resulting topics and the email corpus.
+First, can we identify a sensible structure in our topics that captures the structure we see with spectral clustering?
+Second, can we identify informative content topics that correspond to real world events?
+Finally, can we say anything about the email senders based on the topics discussed?
 
 \subsection{Interpreting Topics}
-Include ``grunt work'' of interpreting topics, topic frequency
+
+MERGE HERE
+
+ALSO TOPIC TABLE
+
+At first, it may seem alarming that there are common and weak topics, but it's actually a good thing in many ways.
+First, it's remarkable and incredibly useful from an analysis standpoint, that LDA accurately separates the common words into their own topics.
+Clearly, words like ``think'', ``like'', and ``good'' are going to be present in any collection of documents, and they're not common enough like ``a'', ``and'', ``the'' to just eliminate from the data.
+This means LDA is capable of separating out common words into their own topics so they can be incorporated or ignored as seen fit.
+This is a huge advantage of this method.
+
+As for the weak topics, not every topic has many, many words associated with it, so it's natural for some topics to have less words associated necessitating the algorithm to fill them in with other words.
+For example, both terrorism topics are in the weak category.
+Domestic terror at first glance could be a common category, but there are words below that seen such as ``death'', ``student'', ``group'', and ``hospit'' among others that help identify as Domestic Terror.
+Topics such as this can come about as a common-sense thought that ``Domestic Terror'' should be a topic among Hillary Clinton's emails and this was the strongest of the weaker topics to fit this idea.
+Is this right, or correct to label a topic in this manner?
+There is no right or wrong in this sense when it comes down to it.
+There is no statistical procedure that outlines the labeling of topics, so it is all done by eye.
+
+After the initial run-through to label each topic, more summary can be done to further categorize the various topics.
+Looking through, we can place the topics together, see table \ref{tab:topic_cat} for these groups.
 
@@
 \end{table}
+
+The second thing that LDA gives is, for each email, a probability for every topic that the topic is included in the email.
+Here, we will look at the relationships between topics and the frequencies that the topics are discussed.
+
+If we look at the entire data set, LDA will not give any topics probabilities of zero for any email, even if that topic realistically doesn't come up at all.
+For example, here are the first six emails in the data set with the probabilities (in percent here) that each of the 30 topics is discussed in the email.
+
+PROBABILITY TABLE
+
+A few things jump out.
+First, every topic is at least 1\% in each email (at least apparently in this grouping, but it's this way throughout the entire set).
+Second, some emails aren't about very much at all.
+Email 1 has 3\% for everything and 9\% for topic 3, which was a common topic.
+Contrast this with email 2, which has a low \% for every topic except 18, 19, 21, 25.
+We could hypothesize that this email is about the Middle East, Foreign Policy, and Domestic Politics.
+We could, of course, do this kind of procedure with email after email, but with 28,000 emails we need a way to get meaning from the whole group.
+
+Before analyzing, we will remove the percentages for the common topics for each email, since we can realistically say that no email is about a topic with ``can'', ``also'', ``will'', etc., as the key words.
+Next, we will zero any topic for each email that has less than 5\%.
+The reason for this is the same as the logic in the above paragraph.
+For email 2, we would naturally seek the topics with the higher percentages and ignore the rest.
+After this we will rescale the percentages.
+
+First, we can look at the number of emails that had each of the 26 non-common topics as the primary topic, or the topic with the highest percentage associated with it.
 
@@
 
+As we can see, the color-coding catches the eye, and the first unmistakable observation we can make is that Hillary Clinton and her staff talk a lot about meetings.
+This is probably not too surprising for someone in her level of the US government.
+As a high level official like Secretary of State, much of her day is probably spent in some sort of meeting or briefing getting filled in by her subordinates.
+
+Another quick observation that we can make is that there is a stark absence of domestic politics type issues such as abortion, health care, domestic economy, and others.
+This, also, is not too surprising, as Hillary Clinton was Secretary of State, a position that mainly consists of foreign affairs.
+
+Speaking of foreign affairs, the topic frequency for the purple above is much less than we might expect, except for 21.
+This could be perceived as a bit unexpected from the Secretary of State.
+This generalization might be unfair, however, because other specific foreign affair topics like 18 and 29 are higher and are about, for example, the Middle East.
+
 \subsection{Types of Topics}
@@
 \subsection{Topic Analysis}
-Analyze some specific topics, compare use over time and how it correlates with related events
+
+We next want to get a sense of what the content topics look like and whether they correspond to real world events.
+See table \ref{tab:content_topics}, for the top 10 words for a subset of six topics that we consider content topics.
+These topics correspond to real world politically significant events.
+For instances the Libya topic captures information about the Benghazi scandal as well the collapse of Gaddafi's administration.
 
@@
 \centering
-\label{topic_top_words}
 \scalebox{0.8}{
@@
 \end{table}
+
+Looking at the table we can see that the model does a good job of identifying words that we as human observers would associate with these events.
+The election topic picks up on both of the primary political parties in the United States as well as words associated with political parties and elections, eg.
+polit(ics), parti(y), elect(ion), percent, candid(ate).
+Similarly, the international development topics identifies words that we would associate with international development, eg.
+develop, support, global.
+While this is only a subset of the content topics, we find that all of our content topics have this pattern.
+
+While our content topics do appear to be sensible, we also want to get a sense of whether our topics appear in correct location in time.
+For email we have a time stamp so we can sort our topic proportions by time to get a sense of whether our topics line up with real world events that correspond to the human interpretation of our topics.
+See figure \ref{fig:topic_time_plots} for a plot of the mean monthly topic proportion fo the subset of content topics discussed above.
+
+Comparing our topic proportion plots to real world news events, we can see that our topics do a good job of picking up on the correct events.
+In the Isreal topic the first peak of the topic proportions corresponds to the July 26th, 2010 joint Israeli and Romanian helicopter disaster, while the second peak corresponds to the September 9th, 2011 attack on the Israel embassy in Egypt.
+Similarly, for the election topic each of the peaks corresponds to an election in the US.
+Finally, the first peak of the Libya topic corresponds to the fall of Gaddafi's adminstration in October of 2011, while the second peak corresponds to the Benghazi attack on September 11th, 2012.
+Again, while this shows only a subset of the topics we find that this pattern persists throughout our content topics\footnote{Comparable topic proportion plots are available on the github page for this project.}.
 
@@
 \end{subfigure}
+\caption{Visualization of the average monthly topic proportion for a subset of content topics over time.}
 \label{fig:topic_time_plots}
@@
 \section{Email Sender Prediction}
-Talk about the who says what table
+
+Finally, we want to consider whether we can say anything interesting about the senders based on our topic model.
+In total 395 unique senders exist in our email corpus, however, only 14 senders sent more than 100 emails.
+We focus on this subset of 14 senders for the remainder of our analysis.
+This leaves us with a corpus of 25809 emails.
+We use the topic proportions from the model estimated on the full corpus for this subset.
 
@@
 }
-\caption{Primary sources for interesting topics}
-\label{tab:top_sources}
+\caption{Primary senders for interesting topics}
+\label{tab:top_senders}
 \end{table}
 
+See table \ref{tab:top_senders} for a ranking of the 14 senders for the subset of content topics explored above.
+This table presents the top five senders for each of the topics based on the average topic proportion for each sender.
+The sorting that we get back seems to fit with a human understanding of each of the senders, Sidney Blumenthal, who appears to be most associated with the Israel, Election and Obama topics is a long standing advisor to the Clinton family who has written extensively on US politics as well as foreign policy.
+Similarly, Huma Abedin, who is most associated with Libya was a key figure during the Benghazi hearings and was generally strongly associated with foreign policy, particularlly in the Middle East while Hillary Clinton's Deputy Chief of Staff.
+Finally, Judith McHale, who is most associated with the Afghanistan and international development topic was Under Secretary of State for Public Diplomacy and Public Affairs during the early portion of the email corpus under Hillary.
+She also has been strongly associated with a number of philanthropic efforts.
+It may be interesting to note that Hillary does not appear to be strongly associated with many of our subset of content topics.
+This pattern persists through the remainder of the content topics, in general, Hillary does not appear to send many emails strongly associated with most of the content topics.
+
 \subsection{Multinomial Logistic Regression}
-Quickly describe model and discuss results
+
+While the above results do give some sense of which senders are most associated with which topics, we next want to formalize this approach and get more general results that can more easily show us which senders are most related to each topic.
+To approach this problem we turn to multinomial logistic regression as a solution.
+Multinomial logistic regression generalizes the logistic regression approach to the case with more labels than two.
+Part of the output of multinomial logistic regression is a $P \times K$ matrix of coefficients corresponding to how strongly related each of the $K$ variables of interest are related to each of the $P$ labels.
+
+For our particular case we estimate a model using the $30$ topics as our explanatory variables and the $14$ senders as our labels.
+We use a training subset of 23229 emails and their corresponding topic proportions to train our model and a subset of 2580 emails for testing.
+See table \ref{tab:mlr_success} for the success rate for our testing data.
+Overall the model appears to perform well, correctly identifying roughly 30\% of the senders correctly.
+For Hillary we correctly identify 74\% of the emails.
+
+\begin{table}[h]
+\centering
+%\scalebox{0.7}{
+\begin{tabular}{ccc}
+\toprule
+Source & Success Rate & Testing Observations \\
+\midrule
+Hillary Clinton & 0.74 & 849 \\
+Philippe Reines & 0.06 & 34 \\
+Claire Coleman & 0.52 & 27 \\
+Lauren Jiloty & 0.42 & 71 \\
+Huma Abedin & 0.36 & 376 \\
+Jake Sullivan & 0.23 & 410 \\
+Sidney Blumenthal & 0.29 & 87 \\
+Cherly Mills & 0.31 & 491 \\
+Anne-Marie Slaughter & 0.36 & 42 \\
+Monica Hanley & 0.09 & 53 \\
+Judith McHale & 0.25 & 28 \\
+Robert Russo & 0.00 & 10 \\
+Richard Verma & 0.26 & 19 \\
+Wendy Sherman & 0.08 & 12 \\
+Melanne Verveer & 0.30 & 30 \\
+Lona Valmoro & 0.34 & 41 \\
+\bottomrule
+\end{tabular}
+%}
+\caption{Multinomial logistic regression successes}
+\label{tab:mlr_success}
+\end{table}
+
+To relate these results back to our earlier analysis we want to look at the coefficients for the multinomial logistic regression model as this should give us a sense of how strongly each sender is associated with the different topics.
+See figure \ref{fig:coefficients} for a heatmap of the resulting coefficient matrix\footnote{Note that the coefficients are standardized and we threshold all standardized coefficients above or below 2 to make the heatmap easier to interpret.}.
+
+The results we see here all us to tell a story about the email senders that corresponds to our intution based on each of the sender's backgrounds.
+Sidney Blumenthal is strongly associated with the Middle East, foreign policy and general politics topics.
+He doesn't have much to say about Hillary or her significance to the press and generally doesn't talk muhc about meetings.
+Huma Abedin and Jake Sullivan provide advice on the Middle east and foreign policy.
+Judith McHale focuses her emails on foreign policy and handling press issues.
+While all this is going on Hillary spends most of her time discussing meetings.
+
+In general the story that emerges is that while Hillary does not say much herself about world events, she has surrounded herself with a set of advisors who are more than willing to say a great deal about the content topics.
+She then spends most of her time on email coordinating meetings, telling people to print emails and generally coordinating the information gathered from her advisors.
 
@@
 
+We have presented a series of results to attempt to make a large corpus of emails that would be difficult to parse manually approachable to the human user.
+We have been able to identify general structures in the email corpus using both spectral clustering and LDA.
+For LDA we find that we can seperate out content topics from structural topics and that the topics we get back are sensible and align with what we would expect in the real world.
+Additionally, we find that we can say something interesting about the senders for our email corpus.
+
+There are many ways that this work could be expanded, and our work should be considered explorartory and a starting place more than anything else.
+While we begin to dive into some possible extensions when we discuss senders this idea could easily be taken further.
+Information on recievers, while not as clean as sender information could also be incorporated.
+This could allows us to build a better model of interactions within the email corpus.
+Additionally, variables beyond just the topic proportions could be incorporated into our model, one clear example of this is a time spline variable to account for the possibility that different senders are more important for different topics over time.
+
+Overall, we have tried to tell a story about the Hillary email corpus.
+We have only scratched the surface of our understanding of this corpus but we believe that we have layed out a good set of tools and a strong approach to move forward.
+
 \end{document}

### 2016-04-20 paper/paper.tex
local changes

@@
 
-MERGE HERE
+To answer the first question above, we have to turn to human intuition.
+While the original problem was too massive for a human to take on, the LDA algorithm has produced the prescribed number of topics with the most common words for each topic.
+This looks like:
 
-ALSO TOPIC TABLE
+The algorithm of course makes no attempt to interpret the meaning of this, as it simply looks for the words that generally appear together and lumps them into the specified number of topics.
+At this point, we literally have to look through each topic and attempt to identify it.
+For example, topic 6 seems to be about Israel with key words like ``israel'', ``palestinian'', and ``netanyahu'', while topic 8 seems to have a lot of common words like ``think'', ``like'', and ``good''.
+
+After this, we have our overall topic table.
+
+TOPIC TABLE HERE
 

### 2016-04-20 paper/paper.tex
Starting edits.

@@
 To try and move beyond the limitations of spectral clustering and capture some of the content of the emails as well as structure, we next turn to latent Dirichlet allocation (LDA).
-LDA is a popular form of topic modeling that has historically been effective for identifying clusters or "topics" in text corpuses\footnote{note on estimation}.
+LDA is a popular form of topic modeling that has historically been effective for identifying clusters or ``topics'' in text corpuses.\footnote{note on estimation}
 
 LDA requires the number of topics to be specified as an input to the model, therefore one of the preliminary steps for topic model estimation is the selection of an appropriate number of topics.
-Since our ultimate goal was to find sensible topics that could be used to understand the email corpus we initially turned to several coherence measures to perform our model selection, in particular we considered the UMass and UCI measures\footnote{add bib here}.
-Coherence measures were developed as a way to quantify whether topics could make sense to a human observer.
-However, the coherence of our topics didn't appear to vary much assuming we used more than 15 topics and less than 50.
-As a result we turned to manual methods for selecting the number of topics that appeared to perform the best.
-We estimated LDA for 5,10,...,75 topics and selected the model that appeared to be the most sensible to a human observer.
-This left us with a 30 topic model.
+Since our ultimate goal is to find sensible topics that can be used to understand the email corpus, we initially turned to several coherence measures to perform our model selection.
+In particular, we considered the UMass and UCI measures.\footnote{add bib here} Coherence measures allow us to quantify whether estimated topics make sense to a human observer.
+However, the coherence of our topics did not appear to vary much across a wide range of reasonable topic numbers, from roughly 15 to 50 topics used.
+As a result we manually examined the results from models using a range of topics and attempted to select the most parsimonious model, resulting in a 30 topic model.
 
-Using our resulting topic model we want to answer a series of questions concerning our resulting topics and the email corpus.
+% After estimating our final topic model we want to answer a series of questions concerning our resulting topics and the email corpus.
 First, can we identify a sensible structure in our topics that captures the structure we see with spectral clustering?
@@
 
-To answer the first question above, we have to turn to human intuition.
-While the original problem was too massive for a human to take on, the LDA algorithm has produced the prescribed number of topics with the most common words for each topic.
-This looks like:
+After choosing and estimating our topic model, the first task is to check whether we can actually find meaning in the resulting topics.
+If topics correspond to meaningful issues or structures then we can use these results to make useful observations about the data.
+
+This ability to then perform ``human'' analysis on the results is one of the key features of LDA.
+Bringing human intuition to bear on a 28,000 email corpus is nearly impossible, but by condensing the data into a handful of topics LDA has allowed us to leverage our human understanding of semantics and meaning to analyze the data.
+
+Analysis is most easily done by examining the top words from each topics to find patterns and themes. Table~XX shows the top 10 words for each of the 30 estimated topics.
 
@@
 
-\begin{table}[h]
-\centering
-\scalebox{0.8}{
+\begin{table}[h] \centering
 \begin{tabular}{cccccc}
@@
 \end{tabular}
-}
 \caption{Some interesting content topics}
@@
 For email we have a time stamp so we can sort our topic proportions by time to get a sense of whether our topics line up with real world events that correspond to the human interpretation of our topics.
-See figure \ref{fig:topic_time_plots} for a plot of the mean monthly topic proportion fo the subset of content topics discussed above.
+See Figure~\ref{fig:topic_time_plots} for a plot of the mean monthly topic proportion fo the subset of content topics discussed above.
 
@@
 Finally, the first peak of the Libya topic corresponds to the fall of Gaddafi's adminstration in October of 2011, while the second peak corresponds to the Benghazi attack on September 11th, 2012.
-Again, while this shows only a subset of the topics we find that this pattern persists throughout our content topics\footnote{Comparable topic proportion plots are available on the github page for this project.}.
+Again, while this shows only a subset of the topics we find that this pattern persists throughout our content topics.\footnote{Comparable topic proportion plots are available on the github page for this project.}
 
-\begin{figure}[h]
+\begin{figure}[htb]
 \centering
@@
 
-\begin{table}[h]
-\centering
-\label{topic_sources}
-\scalebox{0.70}{
+\begin{table}[htb] \centering \scriptsize
 \begin{tabular}{cccccc}
@@
 \end{tabular}
-}
 \caption{Primary senders for interesting topics}
@@
 
-\begin{table}[h]
-\centering
-%\scalebox{0.7}{
+\begin{table}[htb] \centering
 \begin{tabular}{ccc}
@@
 \end{tabular}
-%}
 \caption{Multinomial logistic regression successes}
@@
 To relate these results back to our earlier analysis we want to look at the coefficients for the multinomial logistic regression model as this should give us a sense of how strongly each sender is associated with the different topics.
-See figure \ref{fig:coefficients} for a heatmap of the resulting coefficient matrix\footnote{Note that the coefficients are standardized and we threshold all standardized coefficients above or below 2 to make the heatmap easier to interpret.}.
+See Figure~\ref{fig:coefficients} for a heatmap of the resulting coefficient matrix.\footnote{Note that the coefficients are standardized and then thresholded at $\pm2$ for illustrative purposes.}
 

### 2016-04-20 paper/paper.tex
Added top words table.

@@
 
-TOPIC TABLE HERE
+\begin{table}[htb] \centering \scriptsize
+\include{top_words_table}
+\caption{Topic Top Words}
+\label{tab:top_words}
+\end{table}
 
@@
 \subsection{Topic Analysis}
-
 We next want to get a sense of what the content topics look like and whether they correspond to real world events.
@@
 
-See table \ref{tab:top_senders} for a ranking of the 14 senders for the subset of content topics explored above.
+See Table~\ref{tab:top_senders} for a ranking of the 14 senders for the subset of content topics explored above.
 This table presents the top five senders for each of the topics based on the average topic proportion for each sender.

### 2016-04-20 paper/top_words_table.tex
Added top words table.

\setlength{\tabcolsep}{4pt}
\begin{tabular}{cccccccccc}
  \toprule
  Topic 1 & Topic 2 & Topic 3 & Topic 4 & Topic 5   & Topic 6     & Topic 7  & Topic 8 & Topic 9   & Topic 10 \\
  \midrule
  call    & mistr   & know    & see     & state     & israel      & peopl    & think   & meet      & discuss  \\
  huma    & last    & just    & report  & benghazi  & isra        & world    & like    & reuters   & letter   \\
  abedin  & said    & want    & haiti   & inform    & peac        & power    & good    & follow    & draft    \\
  schedul & parti   & let     & news    & date      & palestinian & polit    & say     & update    & cdm      \\
  sheet   & david   & ask     & great   & subject   & netanyahu   & mani     & dont    & list      & note     \\
  request & prime   & come    & read    & agreement & east        & right    & look    & happi     & eam      \\
  speak   & deal    & tri     & media   & depart    & negoti      & can      & got     & monday    & secretar \\
  readout & leader  & sure    & event   & doc       & arab        & govern   & tell    & scshedule & question \\
  calls   & govern  & thx     & post    & hous      & state       & one      & thing   & set       & final    \\
  phone   & ireland & best    & connect & produc    & middl       & american & idea    & mtg       & brief    \\
  \bottomrule \\
  \toprule
  Topic 11   & Topic 12  & Topic 13 & Topic 14 & Topic 15 & Topic 16   & Topic 17   & Topic 18 & Topic 19 & Topic 20 \\
  \midrule
  democrat   & women     & new      & will     & make     & secretari  & senat      & libya    & iran     & time \\
  republican & clinton   & foreign  & work     & well     & depart     & bill       & secur    & syria    & press \\
  american   & right     & trip     & week     & take     & office     & vote       & travel   & nuclear  & hrc \\
  polit      & hillari   & told     & need     & way      & room       & health     & libyan   & syrian   & staff \\
  parti      & secretari & import   & next     & point    & state      & care       & iraq     & turkey   & dinner \\
  elect      & year      & agre     & also     & hope     & arriv      & pass       & embassi  & russia   & lona \\
  obama      & state     & high     & plan     & time     & rout       & hous       & attack   & regim    & ambassador \\
  percent    & human     & head     & start    & move     & privat     & john       & kill     & iranian  & close \\
  candid     & day       & later    & issu     & possibl  & offic      & committe   & march    & intern   & monica \\
  poll       & mani      & spoke    & keep     & one      & department & republican & august   & opposit  & remark \\
  \bottomrule \\
  \toprule
  Topic 21 & Topic 22 & Topic 23  & Topic 24 & Topic 25  & Topic 26 & Topic 27    & Topic 28 & Topic 29  & Topic 30 \\
  \midrule
  fyi      & said     & develop   & email    & presid    & china    & afghanistan & can      & statement & tomorrow \\
  print    & book     & state     & offic    & obama     & econom   & pakistan    & talk     & egypt     & today \\
  sid      & one      & support   & sent     & said      & year     & afghan      & get      & egyptian  & cheryl \\
  thank    & year     & global    & messag   & hous      & chines   & militari    & speech   & respond   & sullivan \\
  memo     & two      & program   & pleas    & white     & job      & general     & now      & announc   & jacob \\
  pls      & day      & effort    & may      & administr & million  & karzai      & back     & releas    & wil \\
  latest   & case     & intern    & check    & polici    & countri  & offici      & updat    & elect     & morn \\
  info     & famili   & work      & copi     & aid       & bank     & war         & send     & saudi     & jake \\
  intel    & school   & includ    & forward  & advis     & polici   & forc        & tonight  & reuter    & mill \\
  urgent   & court    & diplomaci & blair    & former    & economi  & nato        & soon     & presid    & confirm \\
  \bottomrule
\end{tabular}
\setlength{\tabcolsep}{6pt}

### 2016-04-20 paper/paper.tex
Editing editing editing.

@@
 
-\subsection{Spectral Clustering}
+\subsection{Spectral Clustering} \label{sec:spec_cluster}
 In order to better identify structure that may exist in the data, we attempt to apply clustering methods.
@@
 By investigating the individual emails, we can also get a sense of what each cluster consists of.
-For instance, clusters 2 and 4 consist of emails related to calls and communication.
+For instance, Clusters~2 and~4 consist of emails related to calls and communication.
 In this arm, those closer to the main central clump contain more conversation, while those farther out are much briefer and directly about the call (e.g.
 ``I'd like to call tomorrow.'').
-Cluster 3 consists entirely of ``minis,'' summaries of the days schedule sent to Clinton each morning.
-Emails from cluster 5 are generally requests to print materials, while those from cluster 6 are forwarded news articles.
+Cluster~3 consists entirely of ``minis,'' summaries of the days schedule sent to Clinton each morning.
+Emails from Cluster~5 are generally requests to print materials, while those from Cluster~6 are forwarded news articles.
 
@@
 On a related note, it does not do a good job separating the ``regular'' emails.
-OVer 5,000 of the 8,000 emails depicted fall into clusters 1 or 8, which essentially consist of all the emails without specific identifiable structure.
+Over 5,000 of the 8,000 emails depicted fall into Clusters~1 or~8, which essentially consist of all the emails without specific identifiable structure.
 Ideally we would be able to further classify these emails according to subject matter, but clustering does not seem suited to this task.
@@
 \section{Topic Modeling}
+To try and move beyond the limitations of spectral clustering and capture some of the content of the emails as well as structure, we next turn to latent Dirichlet allocation (LDA).
+LDA is a popular form of topic modeling that has historically been effective for identifying meaningful ``topics'' in text corpuses.\footnote{note on estimation}
 
-To try and move beyond the limitations of spectral clustering and capture some of the content of the emails as well as structure, we next turn to latent Dirichlet allocation (LDA).
-LDA is a popular form of topic modeling that has historically been effective for identifying clusters or ``topics'' in text corpuses.\footnote{note on estimation}
-
-LDA requires the number of topics to be specified as an input to the model, therefore one of the preliminary steps for topic model estimation is the selection of an appropriate number of topics.
-Since our ultimate goal is to find sensible topics that can be used to understand the email corpus, we initially turned to several coherence measures to perform our model selection.
-In particular, we considered the UMass and UCI measures.\footnote{add bib here} Coherence measures allow us to quantify whether estimated topics make sense to a human observer.
-However, the coherence of our topics did not appear to vary much across a wide range of reasonable topic numbers, from roughly 15 to 50 topics used.
+The primary parameter that we need to specify for LDA is the number of topics.
+Since our ultimate goal is to find sensible topics that can be used to understand the email corpus, we initially turned to coherence measures, which attempt to quantify whether estimated topics would make sense to a human observer.
+In particular, we considered the UMass and UCI measures.\footnote{add bib here} However, the coherence of our topics did not appear to vary much across a wide range of reasonable topic numbers, from roughly 15 to 50 topics used.
 As a result we manually examined the results from models using a range of topics and attempted to select the most parsimonious model, resulting in a 30 topic model.
@@
 
-Analysis is most easily done by examining the top words from each topics to find patterns and themes. Table~XX shows the top 10 words for each of the 30 estimated topics.
-
-The algorithm of course makes no attempt to interpret the meaning of this, as it simply looks for the words that generally appear together and lumps them into the specified number of topics.
-At this point, we literally have to look through each topic and attempt to identify it.
-For example, topic 6 seems to be about Israel with key words like ``israel'', ``palestinian'', and ``netanyahu'', while topic 8 seems to have a lot of common words like ``think'', ``like'', and ``good''.
-
-After this, we have our overall topic table.
+Analysis is most easily done by examining the top words from each topics to find patterns and themes.
+Table~\ref{tab:top_words} shows the top 10 words for each of the 30 estimated topics.
+The LDA algorithm makes no attempt to interpret these meanings, but by viewing them there are several easily distinguishable patterns.
+For example, many of the top words in Topic~6 relate to Israel and Palestine.
+Not every topic is as well-identified as this, and some of the estimated topics are thematically weaker than others, but overall the topics seems to correspond very well to interpretable subjects.
 
@@
 
-At first, it may seem alarming that there are common and weak topics, but it's actually a good thing in many ways.
-First, it's remarkable and incredibly useful from an analysis standpoint, that LDA accurately separates the common words into their own topics.
-Clearly, words like ``think'', ``like'', and ``good'' are going to be present in any collection of documents, and they're not common enough like ``a'', ``and'', ``the'' to just eliminate from the data.
-This means LDA is capable of separating out common words into their own topics so they can be incorporated or ignored as seen fit.
-This is a huge advantage of this method.
+Another useful example is Topic~8, which does not seem to have any semantically meaningful words but primarily consists of ``common'' words like think, good, and tell.
+These ``structural'' topics illustrate one of the key advantages of the LDA model over spectral clustering.
+As we discussed in Section~\ref{sec:spec_cluster}, spectral clustering is only able to identify clusters based on the structure of emails, not their meaning.
+This is presumably because it primarily relies on the distribution of these ``common'' or ``structural'' words.
+By separating these types of words into separate topics, LDA is therefore able to better identify meaning in emails independent of their structure.
 
-As for the weak topics, not every topic has many, many words associated with it, so it's natural for some topics to have less words associated necessitating the algorithm to fill them in with other words.
-For example, both terrorism topics are in the weak category.
-Domestic terror at first glance could be a common category, but there are words below that seen such as ``death'', ``student'', ``group'', and ``hospit'' among others that help identify as Domestic Terror.
-Topics such as this can come about as a common-sense thought that ``Domestic Terror'' should be a topic among Hillary Clinton's emails and this was the strongest of the weaker topics to fit this idea.
-Is this right, or correct to label a topic in this manner?
-There is no right or wrong in this sense when it comes down to it.
-There is no statistical procedure that outlines the labeling of topics, so it is all done by eye.
-
-After the initial run-through to label each topic, more summary can be done to further categorize the various topics.
-Looking through, we can place the topics together, see table \ref{tab:topic_cat} for these groups.
+\subsection{Topic Categorization}
+Looking through the word lists, we can roughly categorize the topics into overarching themes.
+This is obviously a subjective exercise, but is an example of how LDA can enable human, subjective analysis of the data.
+Table~\ref{tab:topic_cat} contains an example categorization.
 
@@
 
-The second thing that LDA gives is, for each email, a probability for every topic that the topic is included in the email.
+% The second thing that LDA gives is, for each email, a probability for every topic that the topic is included in the email.
 Here, we will look at the relationships between topics and the frequencies that the topics are discussed.
 
-If we look at the entire data set, LDA will not give any topics probabilities of zero for any email, even if that topic realistically doesn't come up at all.
+% If we look at the entire data set, LDA will not give any topics probabilities of zero for any email, even if that topic realistically doesn't come up at all.
 For example, here are the first six emails in the data set with the probabilities (in percent here) that each of the 30 topics is discussed in the email.
 
-PROBABILITY TABLE
+% PROBABILITY TABLE
 
-A few things jump out.
+% A few things jump out.
 First, every topic is at least 1\% in each email (at least apparently in this grouping, but it's this way throughout the entire set).
@@
 
-Before analyzing, we will remove the percentages for the common topics for each email, since we can realistically say that no email is about a topic with ``can'', ``also'', ``will'', etc., as the key words.
+% Before analyzing, we will remove the percentages for the common topics for each email, since we can realistically say that no email is about a topic with ``can'', ``also'', ``will'', etc., as the key words.
 Next, we will zero any topic for each email that has less than 5\%.
@@
 
-First, we can look at the number of emails that had each of the 26 non-common topics as the primary topic, or the topic with the highest percentage associated with it.
+In the LDA model, a document is a probability distribution over the available topics.
+We also estimate these topic proportions for each email.
+To get an idea of the most common topics, we identify the ``primary'' topic in each email.\footnote{To identify primary topics, we ignore ``common'' topics as identified in Table~\ref{tab:topic_cat}.
+Then for each email we identify the highest percentage topic as the ``primary'' topic.} Table~\ref{tab:topic_freq} ranks the topics in terms of how frequently they are the primary topic.
 
@@
   \toprule
-  \colsquare[-3pt]{cforeign}{16pt} &
-  \colsquare[-3pt]{cmeet}{16pt} &
-  \colsquare[-3pt]{cmeet}{16pt} &
-  \colsquare[-3pt]{cmeet}{16pt} &
-  \colsquare[-3pt]{cmeet}{16pt} &
-  \colsquare[-3pt]{cmeet}{16pt} &
-  \colsquare[-3pt]{cpress}{16pt} &
-  \colsquare[-3pt]{cmeet}{16pt} &
-  \colsquare[-3pt]{cmideast}{16pt} &
-  \colsquare[-3pt]{cmideast}{16pt} &
-  \colsquare[-3pt]{cstaff}{16pt} &
-  \colsquare[-3pt]{chill}{16pt} &
-  \colsquare[-3pt]{cstaff}{16pt} &
-  \colsquare[-3pt]{cpolitics}{16pt} &
-  \colsquare[-3pt]{cforeign}{16pt} &
-  \colsquare[-3pt]{cmideast}{16pt} &
-  \colsquare[-3pt]{cforeign}{16pt} &
-  \colsquare[-3pt]{cmideast}{16pt} &
-  \colsquare[-3pt]{cterror}{16pt} &
-  \colsquare[-3pt]{cmideast}{16pt} &
-  \colsquare[-3pt]{cforeign}{16pt} &
-  \colsquare[-3pt]{cpolitics}{16pt} &
-  \colsquare[-3pt]{cforeign}{16pt} &
-  \colsquare[-3pt]{cforeign}{16pt} &
-  \colsquare[-3pt]{cpolitics}{16pt} &
-  \colsquare[-3pt]{cterror}{16pt} \\
+  \colsquare[-3pt]{cforeign}{15pt} &
+  \colsquare[-3pt]{cmeet}{15pt} &
+  \colsquare[-3pt]{cmeet}{15pt} &
+  \colsquare[-3pt]{cmeet}{15pt} &
+  \colsquare[-3pt]{cmeet}{15pt} &
+  \colsquare[-3pt]{cmeet}{15pt} &
+  \colsquare[-3pt]{cpress}{15pt} &
+  \colsquare[-3pt]{cmeet}{15pt} &
+  \colsquare[-3pt]{cmideast}{15pt} &
+  \colsquare[-3pt]{cmideast}{15pt} &
+  \colsquare[-3pt]{cstaff}{15pt} &
+  \colsquare[-3pt]{chill}{15pt} &
+  \colsquare[-3pt]{cstaff}{15pt} &
+  \colsquare[-3pt]{cpolitics}{15pt} &
+  \colsquare[-3pt]{cforeign}{15pt} &
+  \colsquare[-3pt]{cmideast}{15pt} &
+  \colsquare[-3pt]{cforeign}{15pt} &
+  \colsquare[-3pt]{cmideast}{15pt} &
+  \colsquare[-3pt]{cterror}{15pt} &
+  \colsquare[-3pt]{cmideast}{15pt} &
+  \colsquare[-3pt]{cforeign}{15pt} &
+  \colsquare[-3pt]{cpolitics}{15pt} &
+  \colsquare[-3pt]{cforeign}{15pt} &
+  \colsquare[-3pt]{cforeign}{15pt} &
+  \colsquare[-3pt]{cpolitics}{15pt} &
+  \colsquare[-3pt]{cterror}{15pt} \\
   21 & 1 & 28 & 30 & 10 & 9 & 4 & 24 & 18 & 29 & 16 & 12 & 20 &
@@
 
-As we can see, the color-coding catches the eye, and the first unmistakable observation we can make is that Hillary Clinton and her staff talk a lot about meetings.
-This is probably not too surprising for someone in her level of the US government.
-As a high level official like Secretary of State, much of her day is probably spent in some sort of meeting or briefing getting filled in by her subordinates.
+There are several interesting observations we can make from Tabels~\ref{tab:topic_cat} and~\ref{tab:topic_freq}.
+An easy one is that many of these emails are about meetings and similar issues.
+This not only makes sense because of Clinton's position as Secretary of State, where she presumably spends a large amount of time in meetings or briefings, but also because these shorter, administrative emails create high volume and are constantly being sent.
 
-Another quick observation that we can make is that there is a stark absence of domestic politics type issues such as abortion, health care, domestic economy, and others.
-This, also, is not too surprising, as Hillary Clinton was Secretary of State, a position that mainly consists of foreign affairs.
+We can also observe that relatively few of the topics are about domestic issues such as health care, the economy, or education.
+Again, this matches what we would expect given that Clinton's position of Secretary of State means that she primarily deals with foreign affairs, which many of the topics are related to.
 
-Speaking of foreign affairs, the topic frequency for the purple above is much less than we might expect, except for 21.
+% Speaking of foreign affairs, the topic frequency for the purple above is much less than we might expect, except for 21.
 This could be perceived as a bit unexpected from the Secretary of State.
@@
 
-\subsection{Types of Topics}
-Talk about structural, common word, and semantic topics, including ``interesting'' vs. ``non-interesting'' topics, discuss strengths of model in comparison to MDS
-
 \subsection{Topic Analysis}
-We next want to get a sense of what the content topics look like and whether they correspond to real world events.
-See table \ref{tab:content_topics}, for the top 10 words for a subset of six topics that we consider content topics.
-These topics correspond to real world politically significant events.
-For instances the Libya topic captures information about the Benghazi scandal as well the collapse of Gaddafi's administration.
+We can also look into specific topics in more detail to see what they consist of and how they might correspond to real-world events.
+Table~\ref{tab:content_topics} shows the top 10 words for six topics that are all examples of content topics.
+In particular, these topics correspond to specific politically significant events or issues.
+For instance, the Libya topic seems to capture discussion about the Benghazi scandal as well the collapse of Gaddafi's administration.
 
@@
   \toprule
+  Topic 6 & Topic 11 & Topic 18 & Topic 27 & Topic 23 & Topic 25 \\
   Israel & Elections & Libya & Afghanistan & Int. Dev. & Obama \\
@@
 
-Looking at the table we can see that the model does a good job of identifying words that we as human observers would associate with these events.
-The election topic picks up on both of the primary political parties in the United States as well as words associated with political parties and elections, eg.
-polit(ics), parti(y), elect(ion), percent, candid(ate).
-Similarly, the international development topics identifies words that we would associate with international development, eg.
-develop, support, global.
-While this is only a subset of the content topics, we find that all of our content topics have this pattern.
+We can see that the model effectively identifies words human observers would associate with these events.
+Topic~11 picks up on both of the primary political parties in the United States as well as other words associated with elections, such as politics, percent, and candidate.
+Similarly, the Topic~23 identifies words that associated with international development, including develop, support, and global.
 
-While our content topics do appear to be sensible, we also want to get a sense of whether our topics appear in correct location in time.
-For email we have a time stamp so we can sort our topic proportions by time to get a sense of whether our topics line up with real world events that correspond to the human interpretation of our topics.
-See Figure~\ref{fig:topic_time_plots} for a plot of the mean monthly topic proportion fo the subset of content topics discussed above.
-
-Comparing our topic proportion plots to real world news events, we can see that our topics do a good job of picking up on the correct events.
-In the Isreal topic the first peak of the topic proportions corresponds to the July 26th, 2010 joint Israeli and Romanian helicopter disaster, while the second peak corresponds to the September 9th, 2011 attack on the Israel embassy in Egypt.
-Similarly, for the election topic each of the peaks corresponds to an election in the US.
-Finally, the first peak of the Libya topic corresponds to the fall of Gaddafi's adminstration in October of 2011, while the second peak corresponds to the Benghazi attack on September 11th, 2012.
-Again, while this shows only a subset of the topics we find that this pattern persists throughout our content topics.\footnote{Comparable topic proportion plots are available on the github page for this project.}
+Given that we have time stamps foe each email, we can also examine how these topics are used over time.
+Figure~\ref{fig:topic_time_plots} plots the mean monthly topic proportion for each of the topics in Table~\ref{tab:content_topics}.
 
@@
 \end{subfigure}
-\caption{Visualization of the average monthly topic proportion for a subset of content topics over time.}
+\caption{Average monthly topic proportions.}
 \label{fig:topic_time_plots}
@@
 
+We can see that our topics seem to be correlated with the expected real-world events.
+The Israel topic's first peak corresponds to the July 26th, 2010 joint Israeli and Romanian helicopter disaster, while the second peak corresponds to the September 9th, 2011 attack on the Israel embassy in Egypt.
+Similarly, for the election topic each of the peaks corresponds to a U.S.
+election.
+Looking at the Libya topic, the first peak corresponds to the fall of Gaddafi's adminstration in October of 2011, while the second peak corresponds to the Benghazi attack on September 11th, 2012.
+These kinds of patterns over time are interesting to verify, and could also be used to identify the prevalent topics of discussion for times when there are not obvious world events driving discussion.\footnote{These monthly topic proportion plots for all our estimate topics are available at \url{https://github.com/lbybee/601_Final_Project/tree/master/images}.}
+
 \section{Email Sender Prediction}
-
 Finally, we want to consider whether we can say anything interesting about the senders based on our topic model.

### 2016-04-20 paper/paper.tex
More editing.

@@
 
-\title{Exploring Hillary Clinton's Emails\thanks{STATS 601 final project.}}
+\title{Exploring Hillary Clinton's Emails\thanks{STATS 601 final project.
+All of the code used to download, process, and analyze the data for this project is available at \url{https://github.com/lbybee/601_Final_Project} and has been open-sourced under the MIT license.}}
 \author{
@@
 }
-\date{\today}
+\date{April 22, 2016}
 
@@
 \subsection{Interpreting Topics}
-
 After choosing and estimating our topic model, the first task is to check whether we can actually find meaning in the resulting topics.
@@
 
-Analysis is most easily done by examining the top words from each topics to find patterns and themes.
+Interpretation is most easily done by examining the top words from each topics to find patterns and themes.
 Table~\ref{tab:top_words} shows the top 10 words for each of the 30 estimated topics.
@@
 
-We can see that the model effectively identifies words human observers would associate with these events.
+The model seems to effectively identify words that human observers would associate with these events.
 Topic~11 picks up on both of the primary political parties in the United States as well as other words associated with elections, such as politics, percent, and candidate.
@@
 \subsection{Multinomial Logistic Regression}
-
 While the above results do give some sense of which senders are most associated with which topics, we next want to formalize this approach and get more general results that can more easily show us which senders are most related to each topic.
@@
 \section{Conclusion}
-
 We have presented a series of results to attempt to make a large corpus of emails that would be difficult to parse manually approachable to the human user.

### 2016-04-20 paper/paper.tex
Minor changes.

@@
 Since our ultimate goal is to find sensible topics that can be used to understand the email corpus, we initially turned to coherence measures, which attempt to quantify whether estimated topics would make sense to a human observer.
-In particular, we considered the UMass and UCI measures.\footnote{add bib here} However, the coherence of our topics did not appear to vary much across a wide range of reasonable topic numbers, from roughly 15 to 50 topics used.
+In particular, we considered the UMass and UCI measures.\footnote{add bib here} However, the coherence of our topics did not appear to vary much across a wide range of reasonable topic numbers, anywhere from 15 to 50 topics used.
 As a result we manually examined the results from models using a range of topics and attempted to select the most parsimonious model, resulting in a 30 topic model.
@@
 
-Given that we have time stamps foe each email, we can also examine how these topics are used over time.
-Figure~\ref{fig:topic_time_plots} plots the mean monthly topic proportion for each of the topics in Table~\ref{tab:content_topics}.
+Given that we have time stamps foe each email, we can also examine how prevalent each topic is over time.
+Figure~\ref{fig:topic_time_plots} shows the mean monthly topic proportion for each of the topics in Table~\ref{tab:content_topics}.
 
@@
 \end{subfigure}
-\begin{subfigure}[Election]{.30\linewidth}
+\begin{subfigure}[Elections]{.30\linewidth}
     \includegraphics[width=\linewidth]{../images/time_plot11.pdf}
-    \caption{Election} \label{fig:t2}
+    \caption{Elections} \label{fig:t2}
 \end{subfigure}
@@
 Looking at the Libya topic, the first peak corresponds to the fall of Gaddafi's adminstration in October of 2011, while the second peak corresponds to the Benghazi attack on September 11th, 2012.
-These kinds of patterns over time are interesting to verify, and could also be used to identify the prevalent topics of discussion for times when there are not obvious world events driving discussion.\footnote{These monthly topic proportion plots for all our estimate topics are available at \url{https://github.com/lbybee/601_Final_Project/tree/master/images}.}
+These kinds of patterns over time are interesting to verify, and could also be used to identify the prevalent topics of discussion for times when there are not obvious world events driving discussion.\footnote{These monthly topic proportion plots for all our estimated topics are available at \url{https://github.com/lbybee/601_Final_Project/tree/master/images}.}
 
@@
 \end{tabular}
-\caption{Multinomial logistic regression successes}
+\caption{Multinomial logistic regression test results.}
 \label{tab:mlr_success}
@@
 He doesn't have much to say about Hillary or her significance to the press and generally doesn't talk muhc about meetings.
-Huma Abedin and Jake Sullivan provide advice on the Middle east and foreign policy.
+Huma Abedin and Jake Sullivan provide advice on the Middle East and foreign policy.
 Judith McHale focuses her emails on foreign policy and handling press issues.

### 2016-04-21 paper/paper.tex
add model background and coherence sources

@@
 \usepackage{tikz}
+\usetikzlibrary{bayesnet}
 
@@
 To try and move beyond the limitations of spectral clustering and capture some of the content of the emails as well as structure, we next turn to latent Dirichlet allocation (LDA).
-LDA is a popular form of topic modeling that has historically been effective for identifying meaningful ``topics'' in text corpuses.\footnote{note on estimation}
+LDA is a popular form of topic modeling that has historically been effective for identifying meaningful ``topics'' in text corpuses.
+See Figure~\ref{fig:lda_graph} for a graphical representation of the model.
+The model assumes that each document can be represented as a mixture of topics, and that each word is drawn based on the topic proportions in the corresponding document.
+$\theta$ represents the topic proportion for each document and $\beta$ represents the topic weights for each word.
+The model is estimated using variational Bayesian methods.
+
+\begin{figure}
+\centering
+\begin{tikzpicture}[scale=1.0, every node/.style={transform shape}]
+\tikzstyle{main}=[circle, minimum size = 10mm, thick, draw =black!80, node distance = 16mm]
+\tikzstyle{connect}=[-latex, thick]
+\tikzstyle{box}=[rectangle, draw=black!100]
+  \node[main] (alpha) {$\alpha$};
+  \node[main] (theta) [right=of alpha] {$\theta$};
+  \node[main] (z) [right=of theta] {$z$};
+  \node[main] (beta) [above=of z] {$\beta$};
+  \node[main, fill=black!10] (w) [right=of z] {$w$};
+  \edge {alpha} {theta};
+  \edge {theta} {z};
+  \edge {z,beta} {w};
+  \plate {words} {(z)(w)} {$N_m$};
+  \plate {docs} {(theta)(z)(w)(words.south east)(words.north west)} {$M$};
+\end{tikzpicture}
+\caption{LDA Graphical Representation}
+\label{fig:lda_graph}
+\end{figure}
 
@@
 Since our ultimate goal is to find sensible topics that can be used to understand the email corpus, we initially turned to coherence measures, which attempt to quantify whether estimated topics would make sense to a human observer.
-In particular, we considered the UMass and UCI measures.\footnote{add bib here} However, the coherence of our topics did not appear to vary much across a wide range of reasonable topic numbers, anywhere from 15 to 50 topics used.
-As a result we manually examined the results from models using a range of topics and attempted to select the most parsimonious model, resulting in a 30 topic model.
+In particular, we considered the UMass and UCI measures.\footnote{David Mimno, Hanna M.
+Wallach, Edmund Talley, Mirian Leenders, and Andrew McCallum.
+Optimizing Semantic Coherence in Topic Models.
+2011.}\footnote{David Newman, Jey Han Lau, Karl Grieser, and Timothy Baldwin.
+Automatic Evaluation of Topic Coherence.
+2010.}
 
@@
 Multinomial logistic regression generalizes the logistic regression approach to the case with more labels than two.
-Part of the output of multinomial logistic regression is a $P \times K$ matrix of coefficients corresponding to how strongly related each of the $K$ variables of interest are related to each of the $P$ labels.
+The probability that the $j$th label is assigned to the $i$th email is,
+
+\begin{equation} \label{eq:smax}
+p(y_i = j | x_i, \boldsymbol{\beta}) = \frac{\exp\{\beta_j^Tx_i\}}{\sum_{1\leq k\leq K} \exp\{\beta_k^Tx_i\}}
+\end{equation}
+
+This produces a $P \times K$ matrix of coefficients, $\boldsymbol{\beta}$, corresponding to how strongly related each of the $K$ variables of interest are related to each of the $P$ labels.
 

### 2016-04-21 paper/paper.tex
Added bibliography.

@@
 See Figure~\ref{fig:lda_graph} for a graphical representation of the model.
-The model assumes that each document can be represented as a mixture of topics, and that each word is drawn based on the topic proportions in the corresponding document.
+The model represents each document as a mixture of topics, each topic as a probability distributions over words in the vocabulary, and therefore each word is drawn based on the topic proportions in the corresponding document.
 $\theta$ represents the topic proportion for each document and $\beta$ represents the topic weights for each word.
-The model is estimated using variational Bayesian methods.
+The model is estimated using variational Bayesian methods \citep[for more details, see][]{bleilafferty09}.
 
@@
 Since our ultimate goal is to find sensible topics that can be used to understand the email corpus, we initially turned to coherence measures, which attempt to quantify whether estimated topics would make sense to a human observer.
-In particular, we considered the UMass and UCI measures.\footnote{David Mimno, Hanna M.
-Wallach, Edmund Talley, Mirian Leenders, and Andrew McCallum.
-Optimizing Semantic Coherence in Topic Models.
-2011.}\footnote{David Newman, Jey Han Lau, Karl Grieser, and Timothy Baldwin.
-Automatic Evaluation of Topic Coherence.
-2010.}
+In particular, we considered two measures, proposed by \citet{mimnoetal11} and \citet{newmanetal11}.
+However, the coherence of our topics did not appear to vary much across a wide range of reasonable topic numbers, anywhere from 15 to 50 topics used.
+As a result we manually examined the results from models using a range of topics and attempted to select the most parsimonious model, resulting in a 30 topic model.
 
@@
 
+\bibliographystyle{apa}
+\bibliography{biblio}
+
 \end{document}

### 2016-04-21 paper/paper.tex
More editing.

@@
 ``I'd like to call tomorrow.'').
-Cluster~3 consists entirely of ``minis,'' summaries of the days schedule sent to Clinton each morning.
+Cluster~3 consists entirely of ``minis,'' summaries of the day's schedule sent to Clinton each morning.
 Emails from Cluster~5 are generally requests to print materials, while those from Cluster~6 are forwarded news articles.
@@
 \section{Topic Modeling}
-To try and move beyond the limitations of spectral clustering and capture some of the content of the emails as well as structure, we next turn to latent Dirichlet allocation (LDA).
+To move beyond the limitations of clustering we use the latent Dirichlet allocation (LDA) model to hopefully capture both the content and structure emails.
 LDA is a popular form of topic modeling that has historically been effective for identifying meaningful ``topics'' in text corpuses.
 See Figure~\ref{fig:lda_graph} for a graphical representation of the model.
-The model represents each document as a mixture of topics, each topic as a probability distributions over words in the vocabulary, and therefore each word is drawn based on the topic proportions in the corresponding document.
+The model represents each document as a mixture of topics, each topic as a probability distribution over words in the vocabulary, and therefore draws each word based on the topic proportions in the document it comes from.
 $\theta$ represents the topic proportion for each document and $\beta$ represents the topic weights for each word.
@@
 However, the coherence of our topics did not appear to vary much across a wide range of reasonable topic numbers, anywhere from 15 to 50 topics used.
-As a result we manually examined the results from models using a range of topics and attempted to select the most parsimonious model, resulting in a 30 topic model.
+As a result we manually examine the results from models using a range of topics and attempt to select the most parsimonious one, resulting in a 30 topic model.
 
@@
 This ability to then perform ``human'' analysis on the results is one of the key features of LDA.
-Bringing human intuition to bear on a 28,000 email corpus is nearly impossible, but by condensing the data into a handful of topics LDA has allowed us to leverage our human understanding of semantics and meaning to analyze the data.
+Bringing human intuition to bear on a 28,000 email corpus is nearly impossible, but by condensing the data into a handful of topics LDA allows us to leverage our human understanding of semantics and meaning to analyze the data.
 
@@
 \end{tabular}
-\caption{Some interesting content topics}
+\caption{Some example content topics}
 \label{tab:content_topics}
@@
 \section{Email Sender Prediction}
-Finally, we want to consider whether we can say anything interesting about the senders based on our topic model.
+Finally, we want to consider how we might incorporate sender information with  our topic model.
 In total 395 unique senders exist in our email corpus, however, only 14 senders sent more than 100 emails.
 We focus on this subset of 14 senders for the remainder of our analysis.
-This leaves us with a corpus of 25809 emails.
+This leaves us with a subset of 25,809 emails.
 We use the topic proportions from the model estimated on the full corpus for this subset.
@@
 \end{tabular}
-\caption{Primary senders for interesting topics}
+\caption{Primary senders for some example topics}
 \label{tab:top_senders}
@@
 
-See Table~\ref{tab:top_senders} for a ranking of the 14 senders for the subset of content topics explored above.
-This table presents the top five senders for each of the topics based on the average topic proportion for each sender.
-The sorting that we get back seems to fit with a human understanding of each of the senders, Sidney Blumenthal, who appears to be most associated with the Israel, Election and Obama topics is a long standing advisor to the Clinton family who has written extensively on US politics as well as foreign policy.
-Similarly, Huma Abedin, who is most associated with Libya was a key figure during the Benghazi hearings and was generally strongly associated with foreign policy, particularlly in the Middle East while Hillary Clinton's Deputy Chief of Staff.
-Finally, Judith McHale, who is most associated with the Afghanistan and international development topic was Under Secretary of State for Public Diplomacy and Public Affairs during the early portion of the email corpus under Hillary.
-She also has been strongly associated with a number of philanthropic efforts.
-It may be interesting to note that Hillary does not appear to be strongly associated with many of our subset of content topics.
-This pattern persists through the remainder of the content topics, in general, Hillary does not appear to send many emails strongly associated with most of the content topics.
+Table~\ref{tab:top_senders} presents the top five senders for each of several example topics based on the average topic proportions for each sender.
+The sorting that we get back seems to fit our understanding of the senders.
+For example, Sidney Blumenthal, who appears to be most associated with the Israel, Election and Obama topics is a long standing advisor to the Clinton family who has written extensively on U.S.
+politics as well as foreign policy.
+Similarly, Huma Abedin, who is most associated with Libya, was a key figure during the Benghazi hearings and was generally strongly associated with foreign policy (especially regarding the Middle East) while serving as Hillary Clinton's Deputy Chief of Staff.
+Judith McHale, who is most associated with the Afghanistan and international development topics, was Under Secretary of State for Public Diplomacy and Public Affairs during the early portion of of the 2008-2013 time period.
+She has also been strongly associated with a number of philanthropic efforts.
+
+It is interesting to note that Clinton does not appear to be strongly associated with any of these content topics.
+This pattern persists through the remainder of the content topics; in general, Cliton does not appear to send nearly as many emails strongly associated with content topics as she receives.
 
@@
 While the above results do give some sense of which senders are most associated with which topics, we next want to formalize this approach and get more general results that can more easily show us which senders are most related to each topic.
-To approach this problem we turn to multinomial logistic regression as a solution.
-Multinomial logistic regression generalizes the logistic regression approach to the case with more labels than two.
-The probability that the $j$th label is assigned to the $i$th email is,
+To approach this problem we use multinomial logistic regression.
+Multinomial logistic regression generalizes the logistic regression approach to cases with more than two outcome labels.
+The probability that the $j$th label is assigned to the $i$th email is
+\begin{equation} \label{eq:smax}
+p(y_i = j \cond x_i, \bmath{\beta}) = \frac{\exp \left( \beta_j^T x_i \right)}{\sum_{k=1}^K \exp \left( \beta_k^T x_i \right)}
+\end{equation}
+This produces a $P \times K$ matrix of coefficients, $\bmath{\beta}$, corresponding to how strongly related each of the $K$ variables of interest are related to each of the $P$ labels.
 
-\begin{equation} \label{eq:smax}
-p(y_i = j | x_i, \boldsymbol{\beta}) = \frac{\exp\{\beta_j^Tx_i\}}{\sum_{1\leq k\leq K} \exp\{\beta_k^Tx_i\}}
-\end{equation}
-
-This produces a $P \times K$ matrix of coefficients, $\boldsymbol{\beta}$, corresponding to how strongly related each of the $K$ variables of interest are related to each of the $P$ labels.
-
-For our particular case we estimate a model using the $30$ topics as our explanatory variables and the $14$ senders as our labels.
-We use a training subset of 23229 emails and their corresponding topic proportions to train our model and a subset of 2580 emails for testing.
-See table \ref{tab:mlr_success} for the success rate for our testing data.
+For our particular case we estimate a model using the 30 topics as our explanatory variables and the 14 senders as our labels.
+We use a training subset of 23,229 emails and their corresponding topic proportions to train our model and a subset of 2,580 emails for testing.
+See Table~\ref{tab:mlr_success} for the success rate for our testing data.
 Overall the model appears to perform well, correctly identifying roughly 30\% of the senders correctly.
-For Hillary we correctly identify 74\% of the emails.
+For test emails sent by Clinton we correctly identify the sender 74\% of the time.
 
@@
 
-To relate these results back to our earlier analysis we want to look at the coefficients for the multinomial logistic regression model as this should give us a sense of how strongly each sender is associated with the different topics.
-See Figure~\ref{fig:coefficients} for a heatmap of the resulting coefficient matrix.\footnote{Note that the coefficients are standardized and then thresholded at $\pm2$ for illustrative purposes.}
-
-The results we see here all us to tell a story about the email senders that corresponds to our intution based on each of the sender's backgrounds.
-Sidney Blumenthal is strongly associated with the Middle East, foreign policy and general politics topics.
-He doesn't have much to say about Hillary or her significance to the press and generally doesn't talk muhc about meetings.
-Huma Abedin and Jake Sullivan provide advice on the Middle East and foreign policy.
-Judith McHale focuses her emails on foreign policy and handling press issues.
-While all this is going on Hillary spends most of her time discussing meetings.
-
-In general the story that emerges is that while Hillary does not say much herself about world events, she has surrounded herself with a set of advisors who are more than willing to say a great deal about the content topics.
-She then spends most of her time on email coordinating meetings, telling people to print emails and generally coordinating the information gathered from her advisors.
+The estimated coefficients from the multinomial logistic regression model give us a sense of how strongly each sender is associated with the different topics.
+See Figure~\ref{fig:coefficients} for a visualization of the resulting coefficient matrix.\footnote{Note that the coefficients are standardized and then thresholded at $\pm2$ for illustrative purposes.}
 
@@
 
+The results we see here all us to tell a story about the email senders that corresponds to our intution based on each of the senders' backgrounds.
+Sidney Blumenthal is strongly associated with the Middle East, foreign policy and general politics topics.
+He does not have much to say about Clinton, her significance to the press, or administrative topics such as meetings.
+Huma Abedin and Jake Sullivan provide advice on the Middle East and foreign policy.
+Judith McHale focuses her emails on foreign policy and handling press issues.
+And, as discussed before, Clinton herself primarily sends emails about meetings.
+
+The pattern that seems to emerge from these explorations is that Clinton herself does not discuss world events.
+Instead, she has surrounded herself with a set of advisors who constantly inform her about issues while she mostly uses email to coordinate meetings and calls where (presumably) she does her real work.
+
 \section{Conclusion}
-We have presented a series of results to attempt to make a large corpus of emails that would be difficult to parse manually approachable to the human user.
+The release of the emails from the Clinton family server has provided us with an unprecedented and incredibly interesting and relevant dataset to explore.
+We have used statistical methods to condense this large corpus of emails so that analysis is approachable to the human user.
 We have been able to identify general structures in the email corpus using both spectral clustering and LDA.
-For LDA we find that we can seperate out content topics from structural topics and that the topics we get back are sensible and align with what we would expect in the real world.
-Additionally, we find that we can say something interesting about the senders for our email corpus.
+For LDA we find that we can seperate content topics from structural ones and that the topics we get back are sensible and align with what we would expect.
+Additionally, we have applied simpler statistical methods to the results from LDA to make conclusions about email senders in our corpus.
 
-There are many ways that this work could be expanded, and our work should be considered explorartory and a starting place more than anything else.
-While we begin to dive into some possible extensions when we discuss senders this idea could easily be taken further.
-Information on recievers, while not as clean as sender information could also be incorporated.
-This could allows us to build a better model of interactions within the email corpus.
-Additionally, variables beyond just the topic proportions could be incorporated into our model, one clear example of this is a time spline variable to account for the possibility that different senders are more important for different topics over time.
+There are many ways that this work could be expanded, and our work should be considered exploratory and a starting place.
+The amount of additional questions and topics that could be explored in this dataset is essentially endless, and the following are only a couple more potential starting points.
+Information on recievers, while not as clean as sender information, could also be incorporated and explored.
+This could help build a better model of interactions within the email corpus, possibly even incorporating network information.
+Additionally, LDA itself can be extended in a variety of ways.
+Some examples include time-varying topics, time-varying topic frequencies, or even modeling the topic or word usage of individual senders.
 
-Overall, we have tried to tell a story about the Hillary email corpus.
-We have only scratched the surface of our understanding of this corpus but we believe that we have layed out a good set of tools and a strong approach to move forward.
+Overall, we have started some explorations but have only scratched the surface of possible analysis that could be performed on the Hillary Clinton email corpus.
+We have demonstrated some of the important tools that can be used for future summary and analysis.
 

### 2016-04-21 paper/paper.tex
some editing

@@
 \section{Introduction}
-From roughly 2008 to 2013, Hillary Clinton and some of her staff used a private family email server for most of he communication.
+From roughly 2008 to 2013, Hillary Clinton and some of her staff used a private family email server for most of their communication.
 This time period includes her tenure as U.S.
 Secretary of State, and has therefore become a controversial topic due to the possible security concerns of not using official government servers.
-Various investigations into the legality and appropriateness of the email server have been launched, and the issue has had/will potentiall have a large effect on Clinton's ongoing presidential campaign.
+Various investigations into the legality and appropriateness of the email server have been launched, and the issue has had and will potentially have a significant effect on Clinton's ongoing presidential campaign.
 
-Due to several Freedom of Information Act (FOIA), the State Department has released the vast majority of the roughly 55,000 pages of emails to the public, leading to an unprecedented opportunity to explore the email usage of a major public figure.
+Due to the Freedom of Information Act (FOIA), the State Department has released the vast majority of the roughly 55,000 pages of emails to the public, leading to an unprecedented opportunity to explore the email usage of a major public figure.
 
@@
 In particular, these topics correspond to specific politically significant events or issues.
-For instance, the Libya topic seems to capture discussion about the Benghazi scandal as well the collapse of Gaddafi's administration.
+For instance, the Libya topic seems to capture discussion about the Benghazi scandal as well the collapse of Muammar Gaddafi's administration.
 
@@
   \toprule
+  Topic 6     & Topic 11   & Topic 18 & Topic 27    & Topic 23  & Topic 25 \\
   Israel      & Elections  & Libya    & Afghanistan & Int. Dev. & Obama \\
